### 2022-09-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@2790ad5c56e911605cd8ce75ffa9b998f2d96f02 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{introbackground}{%
\section{Intro/Background}\label{introbackground}}

stuff - why we even have probabilistic networks to start with (or
something like that).

\begin{quote}
probably a dope conceptual figure
\end{quote}

\hypertarget{overview-of-probabilities-and-metawebs}{%
\section{Overview of Probabilities and
Metawebs}\label{overview-of-probabilities-and-metawebs}}

How are we defining what the probability of an interaction is (there are
many ways to slice this cake). What does a probability in the context of
a metaweb mean? Can we turn this into a local network realisation that
is also probabilistic and intuitive?

\hypertarget{non-ecological-networks}{%
\section{Non-ecological Networks}\label{non-ecological-networks}}

What can we learn from other systems/fields \emph{e.g.} social networks,
probabilistic graph theory?

\hypertarget{ecological-context-of-probabilisitic-interactions}{%
\section{Ecological Context of Probabilisitic
Interactions}\label{ecological-context-of-probabilisitic-interactions}}

A cautionary tale of how we define probabilities?

\hypertarget{scaling}{%
\section{Scaling}\label{scaling}}

Regional can inform local but can local inform regional?

\begin{quote}
empirical example figure
\end{quote}

\hypertarget{concluding-notes}{%
\section{Concluding Notes}\label{concluding-notes}}

what even are probabilities? What is the probability that we will ever
know the answer to that?

\hypertarget{references}{%
\section{References}\label{references}}

\end{document}

### 2022-09-07 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@2790ad5c56e911605cd8ce75ffa9b998f2d96f02 🚀

--- 2022-09-07 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{3,4}, %
 Merriadoc\,Brandybuck%
@@
 \,\textsuperscript{5,4,‡}
-
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
-
+\vskip 1em
+\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
+Prancing Pony; \textsuperscript{4}\,Fellowship of the
+Ring; \textsuperscript{5}\,Green Dragon Inn\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2022-09-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@19c4344232e59c0b654415ecee53f4854f83c201 🚀

@@
 
-stuff - why we even have probabilistic networks to start with (or
-something like that).
+Why it is useful think about interactions as probabilistic event An
+interaction is probabilistic since two species `meeting' does not mean
+that an interaction will occur e.g.~a lion crossing paths with a gazelle
+does not mean predation will happen but is contextual on the
+physiological state of both the lion and the gazelle. Also, two species
+co-occurring does not mean there's gonna meet (think of species relative
+abundances)
+
+Aim: Although it makes sense to think about interactions as
+probabilities it is not without challenges. This paper aims to outline
+some of these challenges/limitations of interpreting these probabilities
 
 \begin{quote}
-probably a dope conceptual figure
+probably a dope conceptual figure {[}`scale' up a the nodes from and
+individual to population to taxo group how would how we interpret these
+probabilities change{]}
 \end{quote}
 
-\hypertarget{overview-of-probabilities-and-metawebs}{%
-\section{Overview of Probabilities and
-Metawebs}\label{overview-of-probabilities-and-metawebs}}
+\hypertarget{overview-of-probabilities}{%
+\section{Overview of Probabilities}\label{overview-of-probabilities}}
 
-How are we defining what the probability of an interaction is (there are
-many ways to slice this cake). What does a probability in the context of
-a metaweb mean? Can we turn this into a local network realisation that
-is also probabilistic and intuitive?
+How are we defining (in the literature) what the probability of
+interaction is (there are many ways to slice this cake)? Weighted
+Networks??? It might not be as intuitive as you would think/assume
 
-\hypertarget{non-ecological-networks}{%
-\section{Non-ecological Networks}\label{non-ecological-networks}}
+\hypertarget{probabilistic-metawebs}{%
+\section{Probabilistic Metawebs}\label{probabilistic-metawebs}}
 
-What can we learn from other systems/fields \emph{e.g.} social networks,
-probabilistic graph theory?
+What does a probability in the context of a metaweb mean? Can we turn
+this into a local network realisation that is also probabilistic and
+intuitive? Bayesian vs frequentist
 
@@
 
-A cautionary tale of how we define probabilities?
+A cautionary tale of how we define probabilities? Environmental context,
+local abundance context Talk about individual scale and the population
+scale (probability at the individual level vs the species level)
+Taxonomic scale {[}`scale' up the nodes from an individual to population
+to taxo group how would we interpret these probabilities change. How
+does the aggregation change the interpretation? Does it?{]} How is it
+analogous to spatial and temporal scaling (basically, all kinds of
+scaling are just different ways to aggregate individuals/nodes).
 
@@
 
-Regional can inform local but can local inform regional?
+Note scaling can refer to both space and time Regional can inform local
+but can local inform regional? Network area relationships (Ontario
+lakes?? Or Alaska) Why probabilistic realised networks scale with area
+but not probabilistic metawebs
 
@@
 
-what even are probabilities? What is the probability that we will ever
-know the answer to that?
+\emph{Non-ecological Networks:} What can we learn from other
+systems/fields e.g. social networks, probabilistic graph theory?
+
+What even are the probabilities? What is the probability that we will
+ever know the answer to that?
+
+Be careful how we define probabilities. Be sure to be explicit about
+these things/think about it carefully. Also, different interpretations
+imply different scaling, and different ways to manipulate these numbers.
+\emph{Maybe mention/thinking about workflow from metaweb to realisation}
+
+Scores vs probabilities
 

### 2022-09-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@50314361c67a72be1571b90371ae82559fc540fd 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily The biological interpretation of probabilistic
+ecological networks}
 \vskip 5em
@@
 %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{1,2,3,‡}\quad %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{1,3,‡}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{1,2,‡}\quad %
-Peregrin\,Took%
-%
-\,\textsuperscript{3,4}\quad %
-Merriadoc\,Brandybuck%
-%
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{1,3}
 
 \textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
+Montréal\quad \textsuperscript{2}\,Université de
+Sherbrooke\quad \textsuperscript{3}\,Quebec Centre for Biodiversity
+Science
 
@@
 \textbf{Correspondance to:}\\
-Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+Francis Banville --- \texttt{francis.banville@umontreal.ca}\\
 
@@
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+        {\bfseries 1.:}\,Community ecologists are increasingly shifting
+from a binary thinking of ecological networks (e.g., do species
+interact?) to a more probabilistic perspective (e.g., how likely are
+species to interact?). Assuredly, the benefits of representing
+ecological interactions as probabilistic events are numerous, from a
+better assessment of the spatial variation of interactions to an
+increase capacity to reconstruct networks from sparse data.\\%
+        {\bfseries 2.:}\,However, probabilities need to be used with
+caution when working with ecological networks. Indeed, depending on the
+system at hand and the method used to built probabilistic networks,
+probabilities can have different interpretations that imply different
+ways to manipulate them. This is rarely discussed in the literature,
+thus impeding our ability to use data on probabilistic interactions
+appropriately.\\%
+        {\bfseries 3.:}\,At the core of these differences lie the
+distinction between assessing if two groups of individuals \emph{can}
+interact or if they \emph{will} interact. This impacts the spatial,
+temporal, and taxonomic scaling of interaction probabilities, thus
+enlightening the need to properly define them in their ecological
+context.\\%
+        {\bfseries 4.:}\,With these challenges in mind, we call for a
+better definition and conceptualization of probabilistic ecological
+networks, both at the local and regional scales, and propose a general
+approach to thinking about probabilities in regards to ecological
+interactions.\\%
 

### 2022-09-19 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@50314361c67a72be1571b90371ae82559fc540fd 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{The biological interpretation of
+probabilistic ecological networks}}}
 
@@
 %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{1,2,3,‡}, %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{1,3,‡}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{1,2,‡}, %
-Peregrin\,Took%
-%
-\,\textsuperscript{3,4}, %
-Merriadoc\,Brandybuck%
-%
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{1,3}
 \vskip 1em
-\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
-Prancing Pony; \textsuperscript{4}\,Fellowship of the
-Ring; \textsuperscript{5}\,Green Dragon Inn\\
+\textsuperscript{1}\,Université de
+Montréal; \textsuperscript{2}\,Université de
+Sherbrooke; \textsuperscript{3}\,Quebec Centre for Biodiversity
+Science\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
@@
 \textbf{Correspondance to:}\\
-Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+Francis Banville --- \texttt{francis.banville@umontreal.ca}\\
 }
@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+ecological networks\\metaweb\\probabilistic networks\\spatial
+scale\\species interactions\\temporal scale\\}
 }
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+        {\bfseries 1.:}\,Community ecologists are increasingly shifting
+from a binary thinking of ecological networks (e.g., do species
+interact?) to a more probabilistic perspective (e.g., how likely are
+species to interact?). Assuredly, the benefits of representing
+ecological interactions as probabilistic events are numerous, from a
+better assessment of the spatial variation of interactions to an
+increase capacity to reconstruct networks from sparse data.\\%
+        {\bfseries 2.:}\,However, probabilities need to be used with
+caution when working with ecological networks. Indeed, depending on the
+system at hand and the method used to built probabilistic networks,
+probabilities can have different interpretations that imply different
+ways to manipulate them. This is rarely discussed in the literature,
+thus impeding our ability to use data on probabilistic interactions
+appropriately.\\%
+        {\bfseries 3.:}\,At the core of these differences lie the
+distinction between assessing if two groups of individuals \emph{can}
+interact or if they \emph{will} interact. This impacts the spatial,
+temporal, and taxonomic scaling of interaction probabilities, thus
+enlightening the need to properly define them in their ecological
+context.\\%
+        {\bfseries 4.:}\,With these challenges in mind, we call for a
+better definition and conceptualization of probabilistic ecological
+networks, both at the local and regional scales, and propose a general
+approach to thinking about probabilities in regards to ecological
+interactions.\\%
 

### 2022-09-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@874f7288455de1541869d033d96cf77a2bb42ac3 🚀

@@
 
-        {\bfseries 1.:}\,Community ecologists are increasingly shifting
+        {\bfseries 1:}\,Community ecologists are increasingly shifting
 from a binary thinking of ecological networks (e.g., do species
@@
 increase capacity to reconstruct networks from sparse data.\\%
-        {\bfseries 2.:}\,However, probabilities need to be used with
+        {\bfseries 2:}\,However, probabilities need to be used with
 caution when working with ecological networks. Indeed, depending on the
-system at hand and the method used to built probabilistic networks,
+system at hand and the method used to build probabilistic networks,
 probabilities can have different interpretations that imply different
@@
 appropriately.\\%
-        {\bfseries 3.:}\,At the core of these differences lie the
-distinction between assessing if two groups of individuals \emph{can}
-interact or if they \emph{will} interact. This impacts the spatial,
-temporal, and taxonomic scaling of interaction probabilities, thus
-enlightening the need to properly define them in their ecological
-context.\\%
-        {\bfseries 4.:}\,With these challenges in mind, we call for a
-better definition and conceptualization of probabilistic ecological
-networks, both at the local and regional scales, and propose a general
-approach to thinking about probabilities in regards to ecological
-interactions.\\%
+        {\bfseries 3:}\,At the core of these differences lie the
+distinction between assessing the likelihood that two groups of
+individuals \emph{can} interact and the likelihood that they \emph{will}
+interact. This impacts the spatial, temporal, and taxonomic scaling of
+interaction probabilities, thus further enlightening the need to
+properly define them in their ecological context.\\%
+        {\bfseries 4:}\,With these challenges in mind, we propose a
+general approach to thinking about probabilities in regards to
+ecological interactions, and call for better definitions and
+conceptualizations of probabilistic ecological networks, both at the
+local and regional scales.\\%
 

### 2022-09-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@80025a5d21ec265f30875f53df2db7aef694f593 🚀

@@
 
-\hypertarget{introbackground}{%
-\section{Intro/Background}\label{introbackground}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Why it is useful think about interactions as probabilistic event An
-interaction is probabilistic since two species `meeting' does not mean
-that an interaction will occur e.g.~a lion crossing paths with a gazelle
-does not mean predation will happen but is contextual on the
-physiological state of both the lion and the gazelle. Also, two species
-co-occurring does not mean there's gonna meet (think of species relative
-abundances)
+\hypertarget{general-background}{%
+\subsection{General background}\label{general-background}}
 
-Aim: Although it makes sense to think about interactions as
-probabilities it is not without challenges. This paper aims to outline
-some of these challenges/limitations of interpreting these probabilities
+Why is it useful to think about interactions as probabilistic events?
 
-\begin{quote}
-probably a dope conceptual figure {[}`scale' up a the nodes from and
-individual to population to taxo group how would how we interpret these
-probabilities change{]}
-\end{quote}
+\begin{itemize}
+\tightlist
+\item
+  A biological interaction is probabilistic since two taxa co-occurring
+  does not mean they are going to meet (e.g., think of species relative
+  abundances). Also, two individuals meeting does not mean that an
+  interaction will occur (e.g., a lion crossing paths with a gazelle
+  does not mean predation).
+\item
+  Interaction is contextual on the environment and on the physiological
+  state of both species (or individuals).
+\item
+  Representing ecological interactions as probabilistic events helps us
+  predict networks across time and space and assess the spatial
+  variability of biological interactions.
+\end{itemize}
 
-\hypertarget{overview-of-probabilities}{%
-\section{Overview of Probabilities}\label{overview-of-probabilities}}
+\textbf{Papers:} Poisot \emph{et al.} (2016)
 
-How are we defining (in the literature) what the probability of
-interaction is (there are many ways to slice this cake)? Weighted
-Networks??? It might not be as intuitive as you would think/assume
+\hypertarget{problem-and-objectives}{%
+\subsection{Problem and objectives}\label{problem-and-objectives}}
+
+Why should we use probabilities with caution when working with
+ecological networks? What is the objective of this paper?
+
+\begin{itemize}
+\tightlist
+\item
+  There are different ways to define and interpret interaction
+  probabilities depending on the study system and on the method used to
+  build probabilistic networks.
+\item
+  It is important to document and define what we mean by an interaction
+  probability because different definitions can have different
+  ecological and statistical implications.
+\item
+  This paper aims to outline some of the challenges in interpreting
+  interaction probabilities and propose an approach to thinking about
+  them.
+\end{itemize}
+
+\hypertarget{definitions-and-interpretations}{%
+\section{Definitions and
+interpretations}\label{definitions-and-interpretations}}
+
+\hypertarget{overview-of-interaction-probabilities}{%
+\subsection{Overview of interaction
+probabilities}\label{overview-of-interaction-probabilities}}
+
+How are interaction probabilities defined in the literature? It might
+not be as intuitive as one would think.
+
+\begin{itemize}
+\tightlist
+\item
+  There is a big difference in how we interpret the probability that two
+  species \emph{can} interact (metaweb) and the probability that they
+  \emph{will} interact (realized networks).
+\item
+  Interaction probabilities can be used to describe Boolean interactions
+  (e.g., the probability that two species interact) and weighted
+  interactions (e.g., the probability distribution of the amount of
+  energy flow between two species).
+\item
+  In many studies, it is not obvious if their numbers represent
+  interaction scores or probabilities (in the later case, it is rarely
+  specified what these probabilities truly represent).
+\end{itemize}
 
 \hypertarget{probabilistic-metawebs}{%
-\section{Probabilistic Metawebs}\label{probabilistic-metawebs}}
+\subsection{Probabilistic metawebs}\label{probabilistic-metawebs}}
 
-What does a probability in the context of a metaweb mean? Can we turn
-this into a local network realisation that is also probabilistic and
-intuitive? Bayesian vs frequentist
+What does a probability in the context of a metaweb mean?
 
-\hypertarget{ecological-context-of-probabilisitic-interactions}{%
-\section{Ecological Context of Probabilisitic
-Interactions}\label{ecological-context-of-probabilisitic-interactions}}
+\begin{itemize}
+\tightlist
+\item
+  It means the probability that two taxa can interact, regardless of
+  biological plasticity and environmental variability.
+\item
+  One observation is enough to set this probability to one.
+\item
+  Can we turn this into a local network realisation that is also
+  probabilistic and intuitive?
+\end{itemize}
 
-A cautionary tale of how we define probabilities? Environmental context,
-local abundance context Talk about individual scale and the population
-scale (probability at the individual level vs the species level)
-Taxonomic scale {[}`scale' up the nodes from an individual to population
-to taxo group how would we interpret these probabilities change. How
-does the aggregation change the interpretation? Does it?{]} How is it
-analogous to spatial and temporal scaling (basically, all kinds of
-scaling are just different ways to aggregate individuals/nodes).
+\textbf{Papers:} Strydom \emph{et al.} (2022)
+
+\hypertarget{probabilistic-local-networks}{%
+\subsection{Probabilistic local
+networks}\label{probabilistic-local-networks}}
+
+What does a probability in the context of a local network mean? A
+cautionary tale of how we define probabilities.
+
+\begin{itemize}
+\tightlist
+\item
+  It means the probability that two taxa will interact, regardless of
+  biological plasticity and environmental variability.
+\item
+  What do we mean by two taxa will interact? That at least one
+  individual from one group will interact with (e.g., predate) at least
+  one other individual from the other group.
+\item
+  The probability is conditional on the environmental and local
+  abundance contexts.
+\item
+  We should expect a certain number of interactions to occur depending
+  on the probability value. This number depends on the number of trials,
+  which is defined according to the ecological context (e.g.,
+  environmental conditions, scale) in which probabilities were
+  estimated. This is in contrast with probabilities in metawebs.
+\end{itemize}
 
@@
 
-Note scaling can refer to both space and time Regional can inform local
-but can local inform regional? Network area relationships (Ontario
-lakes?? Or Alaska) Why probabilistic realised networks scale with area
-but not probabilistic metawebs
+\hypertarget{spatial-and-temporal-scales}{%
+\subsection{Spatial and temporal
+scales}\label{spatial-and-temporal-scales}}
 
-\begin{quote}
-empirical example figure
-\end{quote}
+How do interaction probabilities scale spatially and temporally?
 
-\hypertarget{concluding-notes}{%
-\section{Concluding Notes}\label{concluding-notes}}
+\begin{itemize}
+\tightlist
+\item
+  Why do probabilistic local networks scale with area and time but not
+  probabilistic metawebs?
+\item
+  Network area relationships (e.g., Ontario lakes and Alaska datasets)
+\item
+  In metawebs, interaction probabilities do not scale with space and
+  time.
+\item
+  In local networks, interaction probabilities scale with space and
+  time. There are more opportunities of interactions (e.g., more
+  environmental conditions) in a larger area and longer time period.
+\item
+  Regional networks can inform local networks but can local networks
+  inform regional networks?
+\end{itemize}
 
-\emph{Non-ecological Networks:} What can we learn from other
-systems/fields e.g. social networks, probabilistic graph theory?
+\textbf{Figure:} Empirical example of the association between the number
+of interactions in realized local networks and the number of
+interactions in the corresponding species subnetworks of regional
+networks. We should expect the interaction to be linear below the 1:1
+line.
 
+\hypertarget{taxonomic-scale}{%
+\subsection{Taxonomic scale}\label{taxonomic-scale}}
+
+How do interaction probabilities scale taxonomically?
+
+\begin{itemize}
+\tightlist
+\item
+  Difference of interpretation between probabilities in networks at the
+  individual level and at any higher taxonomic level.
+\item
+  How does the scale up of the nodes from an individual to population to
+  taxonomic group group change our interpretation of interaction
+  probabilities? How does the aggregation change the interpretation?
+\item
+  How is it analogous to spatial and temporal scaling? Basically, all
+  kinds of scaling are just different ways to aggregate individuals or
+  nodes.
+\end{itemize}
+
+\textbf{Figure:} Conceptual figure of how a scale up of the nodes from
+an individual to a population to any taxonomic group change our
+interpretation of the probability of interaction.
+
+\hypertarget{concluding-remarks}{%
+\section{Concluding remarks}\label{concluding-remarks}}
+
+Here we present some advice moving forward.
+
+\begin{itemize}
+\tightlist
+\item
+  Non-ecological Networks: What can we learn from other systems/fields
+  (e.g., social networks, probabilistic graph theory)?
+\item
   What even are the probabilities? What is the probability that we will
   ever know the answer to that?
-
+\item
   Be careful how we define probabilities. Be sure to be explicit about
-these things/think about it carefully. Also, different interpretations
-imply different scaling, and different ways to manipulate these numbers.
-\emph{Maybe mention/thinking about workflow from metaweb to realisation}
-
-Scores vs probabilities
+  these things. Be sure to specify the type of interaction, the spatial,
+  temporal, and taxonomic scale when presenting new data on interaction
+  probabilities. We need better metadata documentation.
+\item
+  Be careful to use and manipulate interaction probabilities properly
+  depending on how they were defined. Different interpretations imply
+  different scaling, and thus different ways to manipulate these
+  numbers.
+\item
+  Maybe mention thinking about a workflow to predict probabilistic local
+  networks from probabilistic metawebs.
+\end{itemize}
 
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Poisot2016StrProa}{}%
+Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
+Stouffer, D.B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, 7, 303--312.
+
+\leavevmode\hypertarget{ref-Strydom2022FooWeb}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M.J., \emph{et al.} (2022). Food web reconstruction through phylogenetic
+transfer of low-rank network representation. \emph{Methods in Ecology
+and Evolution}, n/a.
+
+\end{CSLReferences}
 

### 2022-09-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@6cd0d7001a8751ad4718e5d4366c1e20698f6804 🚀

@@
         {\bfseries 2:}\,However, probabilities need to be used with
-caution when working with ecological networks. Indeed, depending on the
-system at hand and the method used to build probabilistic networks,
-probabilities can have different interpretations that imply different
-ways to manipulate them. This is rarely discussed in the literature,
-thus impeding our ability to use data on probabilistic interactions
-appropriately.\\%
+caution when working with interactions and ecological networks. Indeed,
+depending on the system at hand and the method used to build
+probabilistic networks, probabilities can have different interpretations
+that imply different ways to manipulate them. This is rarely discussed
+in the literature, thus impeding our ability to use data on
+probabilistic interactions appropriately.\\%
         {\bfseries 3:}\,At the core of these differences lie the
@@
   probability because different definitions can have different
-  ecological and statistical implications.
+  ecological and statistical implications and final interpretation.
 \item
@@
   In many studies, it is not obvious if their numbers represent
-  interaction scores or probabilities (in the later case, it is rarely
+  interaction scores or probabilities (in the latter case, it is rarely
   specified what these probabilities truly represent).
@@
   It means the probability that two taxa can interact, regardless of
-  biological plasticity and environmental variability.
+  biological plasticity, environmental variability, or co-occurrence.
 \item
@@
 
+\textbf{Papers:} there might be something in these McLeod \emph{et al.}
+(2020); McLeod \emph{et al.} (2021); Wood \emph{et al.} (2015)
+
 \hypertarget{taxonomic-scale}{%
@@
 \item
-  How does the scale up of the nodes from an individual to population to
-  taxonomic group group change our interpretation of interaction
+  How does the scaling up of the nodes from an individual to population
+  to taxonomic group group change our interpretation of interaction
   probabilities? How does the aggregation change the interpretation?
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
+McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
+M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
+of spatial multi-trophic networks. \emph{Oikos}, n/a.
+
+\leavevmode\hypertarget{ref-McLeod2020EffSpe}{}%
+McLeod, A.M., Leroux, S.J. \& Chu, C. (2020). Effects of species traits,
+motif profiles, and environment on spatial variation in multi-trophic
+antagonistic networks. \emph{Ecosphere}, 11, e03018.
+
 \leavevmode\hypertarget{ref-Poisot2016StrProa}{}%
@@
 
+\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
+Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, 5, 3769--3782.
+
 \end{CSLReferences}

### 2022-09-21 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@21e2776218f9a4e3445b3f5611cc8342bffe0545 🚀

@@
 \item
-  It means the probability that two taxa will interact, regardless of
-  biological plasticity and environmental variability.
+  It means the probability that two taxa will interact at a given
+  location.
 \item
@@
   How does the scaling up of the nodes from an individual to population
-  to taxonomic group group change our interpretation of interaction
+  to taxonomic group change our interpretation of interaction
   probabilities? How does the aggregation change the interpretation?
@@
 \item
-  Non-ecological Networks: What can we learn from other systems/fields
+  Non-ecological networks: What can we learn from other systems/fields
   (e.g., social networks, probabilistic graph theory)?
 \item
-  What even are the probabilities? What is the probability that we will
-  ever know the answer to that?
+  What even are probabilities? What is the probability that we will ever
+  know the answer to that?
 \item

### 2022-10-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@8c6a821f3cb0a44605b3671a5a49e50817b182e0 🚀

@@
 {\Large\bfseries\sffamily The biological interpretation of probabilistic
-ecological networks}
+food webs}
 \vskip 5em
@@
         {\bfseries 1:}\,Community ecologists are increasingly shifting
-from a binary thinking of ecological networks (e.g., do species
-interact?) to a more probabilistic perspective (e.g., how likely are
-species to interact?). Assuredly, the benefits of representing
-ecological interactions as probabilistic events are numerous, from a
-better assessment of the spatial variation of interactions to an
-increase capacity to reconstruct networks from sparse data.\\%
+from a binary thinking of food webs and other ecological networks (e.g.,
+do species interact?) to a more probabilistic perspective (e.g., how
+likely are species to interact?). Assuredly, the benefits of
+representing ecological interactions as probabilistic events are
+numerous, from a better assessment of the spatial variation of trophic
+interactions to an increase capacity to reconstruct networks from sparse
+data.\\%
         {\bfseries 2:}\,However, probabilities need to be used with
-caution when working with interactions and ecological networks. Indeed,
-depending on the system at hand and the method used to build
-probabilistic networks, probabilities can have different interpretations
-that imply different ways to manipulate them. This is rarely discussed
-in the literature, thus impeding our ability to use data on
-probabilistic interactions appropriately.\\%
+caution when working with species interactions. Indeed, depending on the
+system at hand and the method used to build probabilistic networks,
+probabilities can have different interpretations that imply different
+ways to manipulate them. This is rarely discussed in the literature,
+thus impeding our ability to use data on probabilistic interactions
+appropriately.\\%
         {\bfseries 3:}\,At the core of these differences lie the
@@
 general approach to thinking about probabilities in regards to
-ecological interactions, and call for better definitions and
-conceptualizations of probabilistic ecological networks, both at the
-local and regional scales.\\%
+ecological interactions, with a strong focus on food webs, and call for
+better definitions and conceptualizations of probabilistic ecological
+networks, both at the local and regional scales.\\%
 
@@
 \item
-  Interaction is contextual on the environment and on the physiological
-  state of both species (or individuals).
+  Species interactions are contextual on the environment and on the
+  physiological state of both species (or individuals).
 \item
-  Representing ecological interactions as probabilistic events helps us
-  predict networks across time and space and assess the spatial
-  variability of biological interactions.
+  Representing trophic interactions as probabilistic events helps us
+  predict food webs across time and space and assess their spatial
+  variability.
 \end{itemize}
@@
 
-Why should we use probabilities with caution when working with
-ecological networks? What is the objective of this paper?
+Why should we use probabilities with caution when working with food webs
+and other ecological networks? What is the objective of this paper?
 
@@
   probabilities depending on the study system and on the method used to
-  build probabilistic networks.
+  build probabilistic food webs.
 \item
@@
   probability because different definitions can have different
-  ecological and statistical implications and final interpretation.
+  ecological and statistical implications and interpretation.
 \item
   This paper aims to outline some of the challenges in interpreting
-  interaction probabilities and propose an approach to thinking about
-  them.
+  interaction probabilities in food webs and propose an approach to
+  thinking about them. Using clear and simple mathematical equations, we
+  distinguish different meanings of probabilistic interactions.
 \end{itemize}
@@
 \item
-  In many studies, it is not obvious if their numbers represent
-  interaction scores or probabilities (in the latter case, it is rarely
-  specified what these probabilities truly represent).
+  In many studies, it is not obvious if authors use interaction scores
+  or probabilities (in the latter case, it is rarely specified what
+  these probabilities truly represent).
 \end{itemize}
@@
 \item
-  What do we mean by two taxa will interact? That at least one
-  individual from one group will interact with (e.g., predate) at least
-  one other individual from the other group.
+  What do we mean by saying that two taxa will interact? We usually mean
+  that at least one individual from one group will interact with (e.g.,
+  predate) at least one other individual from the other group.
 \item
@@
 \item
-  We should expect a certain number of interactions to occur depending
-  on the probability value. This number depends on the number of trials,
-  which is defined according to the ecological context (e.g.,
+  We should expect a certain number of interactions to be realized
+  depending on the probability value. This number depends on the number
+  of trials, which also depends on the ecological context (e.g.,
   environmental conditions, scale) in which probabilities were
@@
 \item
-  Why do probabilistic local networks scale with area and time but not
+  Why do probabilistic local food webs scale with area and time but not
   probabilistic metawebs?
 \item
-  Network area relationships (e.g., Ontario lakes and Alaska datasets)
+  In metawebs, interaction probabilities do not scale with space and
+  time because they depend solely on the biological capacity of two
+  species to interact.
 \item
-  In metawebs, interaction probabilities do not scale with space and
-  time.
-\item
-  In local networks, interaction probabilities scale with space and
-  time. There are more opportunities of interactions (e.g., more
+  In local food webs, interaction probabilities scale with space and
+  time because there are more opportunities of interactions (e.g., more
   environmental conditions) in a larger area and longer time period.
 \item
-  Regional networks can inform local networks but can local networks
-  inform regional networks?
+  What are some network area relationships in probabilistic local food
+  webs?
+\item
+  We know that local networks can inform regional networks. However, can
+  regional networks inform local networks?
 \end{itemize}
@@
 \textbf{Figure:} Empirical example of the association between the number
-of interactions in realized local networks and the number of
+of interactions in realized local food webs and the number of
 interactions in the corresponding species subnetworks of regional
@@
 \item
-  Difference of interpretation between probabilities in networks at the
-  individual level and at any higher taxonomic level.
+  There are different biological interpretations of probabilities in
+  food webs at the individual level and at higher taxonomic levels.
 \item
   How does the scaling up of the nodes from an individual to population
-  to taxonomic group change our interpretation of interaction
-  probabilities? How does the aggregation change the interpretation?
+  to any higher taxonomic group change our interpretation of interaction
+  probabilities? How does the aggregation change our interpretation?
 \item
-  How is it analogous to spatial and temporal scaling? Basically, all
-  kinds of scaling are just different ways to aggregate individuals or
-  nodes.
+  How is it similar and different to spatial and temporal scaling?
+  Basically, all kinds of scaling are just different ways to aggregate
+  individuals or nodes.
 \end{itemize}
@@
 \textbf{Figure:} Conceptual figure of how a scale up of the nodes from
-an individual to a population to any taxonomic group change our
+an individual to a population to any higher taxonomic group change our
 interpretation of the probability of interaction.
@@
 \item
-  Non-ecological networks: What can we learn from other systems/fields
-  (e.g., social networks, probabilistic graph theory)?
+  What can we learn from other systems/fields (e.g., social networks,
+  probabilistic graph theory)?
 \item
@@
 \item
-  Be careful how we define probabilities. Be sure to be explicit about
-  these things. Be sure to specify the type of interaction, the spatial,
-  temporal, and taxonomic scale when presenting new data on interaction
-  probabilities. We need better metadata documentation.
+  Be careful of how we define probabilities. Be sure to be explicit
+  about these things. Be sure to specify the type of interaction, the
+  spatial, temporal, and taxonomic scale when presenting new data on
+  interaction probabilities. We need better metadata documentation.
 \item
   Be careful to use and manipulate interaction probabilities properly
-  depending on how they were defined. Different interpretations imply
-  different scaling, and thus different ways to manipulate these
-  numbers.
+  depending on how they were defined and obtained. Different
+  interpretations imply different scaling, and thus different ways to
+  manipulate these numbers.
 \item
   Maybe mention thinking about a workflow to predict probabilistic local
-  networks from probabilistic metawebs.
+  food webs from probabilistic metawebs.
 \end{itemize}

### 2022-10-14 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@8c6a821f3cb0a44605b3671a5a49e50817b182e0 🚀

@@
 \noindent {\LARGE \textbf{\textsf{The biological interpretation of
-probabilistic ecological networks}}}
+probabilistic food webs}}}
 
@@
 {\small{\bfseries Keywords}:\par
-ecological networks\\metaweb\\probabilistic networks\\spatial
+ecological networks\\food webs\\metaweb\\probabilistic networks\\spatial
 scale\\species interactions\\temporal scale\\}

### 2023-01-26 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0ac08f659b21331459213cd1ce9ba8400f5f6fb3 🚀

@@
 
-\hypertarget{general-background}{%
-\subsection{General background}\label{general-background}}
+Cataloging species interactions across space is a gargantuan task. At
+the core of this challenge lies the spatiotemporal variability of
+ecological networks (Poisot \emph{et al.} 2015), which makes documenting
+the location and timing of interactions difficult. Indeed, it is not
+sufficient to know if two species have the biological capacity to
+interact to infer the realization of this interaction at a specific time
+and space. Taking food webs as an example, a predator and its potential
+prey must first co-occur on the same territory in order for a trophic
+interaction to take place. They must then cross paths, which can happen
+only if their relative abundances in the ecosystem is high enough and
+their phenology matches. Finally, the interaction occurs only if the
+predator has a desire to consume its prey and is able to capture and
+ingest it. Environmental (e.g. temperature and presence of shelters) and
+biological (e.g.~physiological state of both individuals and
+availability of other prey species) factors contribute to this
+variability by impacting species co-occurrence and the realization of
+their interactions. In this context, it is unsurprising that
+computational methods are being developed in ecology to help alleviate
+the colossal sampling efforts required to document species interactions
+across time and space (Strydom \emph{et al.} 2021).
 
-Why is it useful to think about interactions as probabilistic events?
+The recognition of the variability of species interactions and the
+emergence of numerical methods have led ecologists to rethink their
+representation of ecological networks, slowly moving from a binary to a
+probabilistic view of species interactions
+(\textbf{Poisot2016StrProa?}). This has several benefits. For example,
+probabilities represent the limit of our knowledge about species
+interactions and can indicate the expected frequency of two species
+interacting with each other. They are also very helpful in predictive
+models when modeling the spatial distribution and temporal variability
+of ecological networks, generating new ecological data, and identifying
+priority sampling locations.
 
-\begin{itemize}
-\tightlist
-\item
-  A biological interaction is probabilistic since two taxa co-occurring
-  does not mean they are going to meet (e.g., think of species relative
-  abundances). Also, two individuals meeting does not mean that an
-  interaction will occur (e.g., a lion crossing paths with a gazelle
-  does not mean predation).
-\item
-  Species interactions are contextual on the environment and on the
-  physiological state of both species (or individuals).
-\item
-  Representing trophic interactions as probabilistic events helps us
-  predict food webs across time and space and assess their spatial
-  variability.
-\end{itemize}
-
-\textbf{Papers:} Poisot \emph{et al.} (2016)
-
-\hypertarget{problem-and-objectives}{%
-\subsection{Problem and objectives}\label{problem-and-objectives}}
-
-Why should we use probabilities with caution when working with food webs
-and other ecological networks? What is the objective of this paper?
-
-\begin{itemize}
-\tightlist
-\item
-  There are different ways to define and interpret interaction
-  probabilities depending on the study system and on the method used to
-  build probabilistic food webs.
-\item
-  It is important to document and define what we mean by an interaction
-  probability because different definitions can have different
-  ecological and statistical implications and interpretation.
-\item
-  This paper aims to outline some of the challenges in interpreting
-  interaction probabilities in food webs and propose an approach to
-  thinking about them. Using clear and simple mathematical equations, we
-  distinguish different meanings of probabilistic interactions.
-\end{itemize}
+However, representing species interactions probabilistically can also be
+challenging. Beyond methodological difficulties in estimating these
+numbers, there are important conceptual challenges in defining what we
+mean by ``probability of interactions.'' Because this ecological
+representation is still in its infancy, there is no clear definition
+found in the literature. In this contribution, we outline different ways
+to define and interpret interactions probabilities in network ecology
+and propose an approach to thinking about them. These definitions mostly
+depend on the study system (e.g.~local network or metaweb) and on the
+method used to generate them. We show that different definitions can
+have different ecological implications, especially related to spatial,
+temporal, and taxonomic scaling. Although we will focus on food webs,
+our observations and advice can be applied to all types of ecological
+networks, from plant-pollinator to host-parasite networks. Overall, we
+argue that probabilities should be better documented, defined
+mathematically, and used with caution when describing species
+interactions.
 
@@
 
-\textbf{Papers:} Strydom \emph{et al.} (2022)
+\textbf{Papers:} (\textbf{Strydom2022FooWeb?})
 
@@
 \textbf{Papers:} there might be something in these McLeod \emph{et al.}
-(2020); McLeod \emph{et al.} (2021); Wood \emph{et al.} (2015)
+(2020); (\textbf{McLeod2021SamAsy?}); (\textbf{Wood2015EffSpa?})
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
-McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
-M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
-of spatial multi-trophic networks. \emph{Oikos}, n/a.
-
 \leavevmode\hypertarget{ref-McLeod2020EffSpe}{}%
@@
 
-\leavevmode\hypertarget{ref-Poisot2016StrProa}{}%
-Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
-Stouffer, D.B. (2016). The structure of probabilistic networks.
-\emph{Methods in Ecology and Evolution}, 7, 303--312.
+\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, 124, 243--251.
 
-\leavevmode\hypertarget{ref-Strydom2022FooWeb}{}%
-Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
-M.J., \emph{et al.} (2022). Food web reconstruction through phylogenetic
-transfer of low-rank network representation. \emph{Methods in Ecology
-and Evolution}, n/a.
-
-\leavevmode\hypertarget{ref-Wood2015EffSpa}{}%
-Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
-(2015). Effects of spatial scale of sampling on food web structure.
-\emph{Ecology and Evolution}, 5, 3769--3782.
+\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
+Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
+predicting species interaction networks (across space and time).
+\emph{Philosophical Transactions of the Royal Society B-Biological
+Sciences}, 376, 20210063.
 

### 2023-01-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@802ef7496e248930957db84934b8e3bb47c66fe6 🚀

@@
 
-        {\bfseries 1:}\,Community ecologists are increasingly shifting
-from a binary thinking of food webs and other ecological networks (e.g.,
-do species interact?) to a more probabilistic perspective (e.g., how
-likely are species to interact?). Assuredly, the benefits of
-representing ecological interactions as probabilistic events are
-numerous, from a better assessment of the spatial variation of trophic
-interactions to an increase capacity to reconstruct networks from sparse
-data.\\%
-        {\bfseries 2:}\,However, probabilities need to be used with
-caution when working with species interactions. Indeed, depending on the
-system at hand and the method used to build probabilistic networks,
+        {\bfseries 1:}\,Community ecologists are increasingly thinking
+probabilistically when it comes to food webs and other ecological
+networks. Assuredly, the benefits of representing ecological
+interactions as probabilistic events (e.g., how likely are species to
+interact?) instead of binary objects (e.g., do species interact?) are
+numerous, from a better assessment of the spatiotemporal variation of
+trophic interactions to an increase capacity to reconstruct networks
+from sparse data. However, probabilities need to be used with caution
+when working with species interactions. Indeed, depending on the system
+at hand and the method used to build probabilistic networks,
 probabilities can have different interpretations that imply different
-ways to manipulate them. This is rarely discussed in the literature,
-thus impeding our ability to use data on probabilistic interactions
-appropriately.\\%
-        {\bfseries 3:}\,At the core of these differences lie the
+ways to manipulate them. At the core of these differences lie the
 distinction between assessing the likelihood that two groups of
@@
 interact. This impacts the spatial, temporal, and taxonomic scaling of
-interaction probabilities, thus further enlightening the need to
-properly define them in their ecological context.\\%
-        {\bfseries 4:}\,With these challenges in mind, we propose a
-general approach to thinking about probabilities in regards to
-ecological interactions, with a strong focus on food webs, and call for
-better definitions and conceptualizations of probabilistic ecological
-networks, both at the local and regional scales.\\%
+interaction probabilities, thus enlightening the need to properly define
+them in their ecological context. Published data on probabilistic
+species interactions are poorly documented in the literature, which
+impedes our ability to use them appropriately. With these challenges in
+mind, we propose a general approach to thinking about probabilities in
+regards to ecological interactions, with a strong focus on food webs,
+and call for better definitions and conceptualizations of probabilistic
+ecological networks, both at the local and regional scales.\\%
 

### 2023-01-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@77c553fff781e2cc1386dfe1493348f9f35114d5 🚀

@@
 the core of this challenge lies the spatiotemporal variability of
-ecological networks (Poisot \emph{et al.} 2015), which makes documenting
-the location and timing of interactions difficult. Indeed, it is not
-sufficient to know if two species have the biological capacity to
-interact to infer the realization of this interaction at a specific time
-and space. Taking food webs as an example, a predator and its potential
-prey must first co-occur on the same territory in order for a trophic
-interaction to take place. They must then cross paths, which can happen
-only if their relative abundances in the ecosystem is high enough and
-their phenology matches. Finally, the interaction occurs only if the
-predator has a desire to consume its prey and is able to capture and
-ingest it. Environmental (e.g. temperature and presence of shelters) and
-biological (e.g.~physiological state of both individuals and
-availability of other prey species) factors contribute to this
-variability by impacting species co-occurrence and the realization of
-their interactions. In this context, it is unsurprising that
-computational methods are being developed in ecology to help alleviate
-the colossal sampling efforts required to document species interactions
-across time and space (Strydom \emph{et al.} 2021).
+ecological networks (Poisot \emph{et al.} 2012, 2015), which makes
+documenting the location and timing of interactions difficult. Indeed,
+it is not sufficient to know if two species have the biological capacity
+to interact to infer the realization of their interaction at a specific
+time and space {[}TK{]}. Taking food webs as an example, a predator and
+its potential prey must first co-occur on the same territory in order
+for a trophic interaction to take place (Blanchet \emph{et al.} 2020).
+They must then encounter, which is conditional on their relative
+abundances in the ecosystem and the matching of their phenology (Poisot
+\emph{et al.} 2015). Finally, the interaction occurs only if the
+predators have a desire to consume their prey and are able to capture
+and ingest them (Pulliam 1974). Environmental (e.g.~temperature and
+presence of shelters) and biological (e.g.~physiological state of both
+species and availability of other prey species) factors contribute to
+this variability by impacting species co-occurrence {[}TK{]} and the
+realization of their interactions {[}TK{]}. In this context, it is
+unsurprising that computational methods are being developed in ecology
+to help alleviate the colossal sampling efforts required to document
+species interactions across time and space (Strydom \emph{et al.} 2021).
+Having a better portrait of species interactions and the emerging
+structure of food webs is important since it lays the groundwork for
+understanding the functioning {[}TK{]}, dynamics {[}TK{]}, and
+resilience {[}TK{]} of ecosystems worldwide.
 
@@
 interactions and can indicate the expected frequency of two species
-interacting with each other. They are also very helpful in predictive
-models when modeling the spatial distribution and temporal variability
-of ecological networks, generating new ecological data, and identifying
-priority sampling locations.
+interacting with each other {[}TK{]}. They are also very helpful in
+predictive models when modeling the spatial distribution of species
+(Cazelles \emph{et al.} 2016) and the temporal variability of ecological
+networks {[}TK{]}, generating new ecological data (e.g., Strydom
+\emph{et al.} 2022), and identifying priority sampling locations (see
+Andrade-Pacheco \emph{et al.} 2020 for an ecological example of a
+sampling optimization problem). Moreover, the high rate of false
+negatives in ecological network data, resulting from the difficulty of
+witnessing interactions between rare species, makes it hard to interpret
+non-observations of species interactions ecologically (Catchen \emph{et
+al.} 2023). Using probabilities instead of yes-no interactions accounts
+for these observation errors; in that case, only forbidden interactions
+(Jordano \emph{et al.} 2003; Olesen \emph{et al.} 2010) would have a
+probability value of zero (but see Gonzalez-Varo \& Traveset 2016).
 
@@
 numbers, there are important conceptual challenges in defining what we
-mean by ``probability of interactions.'' Because this ecological
-representation is still in its infancy, there is no clear definition
-found in the literature. In this contribution, we outline different ways
-to define and interpret interactions probabilities in network ecology
-and propose an approach to thinking about them. These definitions mostly
-depend on the study system (e.g.~local network or metaweb) and on the
-method used to generate them. We show that different definitions can
-have different ecological implications, especially related to spatial,
-temporal, and taxonomic scaling. Although we will focus on food webs,
-our observations and advice can be applied to all types of ecological
-networks, from plant-pollinator to host-parasite networks. Overall, we
-argue that probabilities should be better documented, defined
-mathematically, and used with caution when describing species
-interactions.
+mean by ``probability of interactions.'' To the best of our knowledge,
+because the building blocks of this mathematical representation of food
+webs are still being laid, there is no clear definition found in the
+literature. This is worrisome, since working with probabilistic species
+interactions without clear guidelines could be misleading as much for
+field ecologists as for computational ecologists who use and generate
+these data. In this contribution, we outline different ways to define
+and interpret interactions probabilities in network ecology and propose
+an approach to thinking about them. These definitions mostly depend on
+the study system (e.g.~local network or metaweb) and on the method used
+to generate them. We show that different definitions can have different
+ecological implications, especially regarding spatial, temporal, and
+taxonomic scaling. Although we will focus on food webs, our observations
+and advice can be applied to all types of ecological networks, from
+plant-pollinator to host-parasite networks. Specifically, we argue that
+probabilities should be better documented, defined mathematically, and
+used with caution when describing species interactions.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Andrade-Pacheco2020FinHot}{}%
+Andrade-Pacheco, R., Rerolle, F., Lemoine, J., Hernandez, L., Meïté, A.,
+Juziwelo, L., \emph{et al.} (2020). Finding hotspots: Development of an
+adaptive spatial sampling approach. \emph{Scientific Reports}, 10,
+10939.
+
+\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
+evidence of ecological interactions. \emph{Ecology Letters}, 23,
+1050--1063.
+
+\leavevmode\hypertarget{ref-Catchen2023MisLin}{}%
+Catchen, M.D., Poisot, T., Pollock, L.J. \& Gonzalez, A. (2023). The
+missing link: Discerning true from false negatives when sampling species
+interaction networks.
+
+\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
+Cazelles, K., Araujo, M.B., Mouquet, N. \& Gravel, D. (2016). A theory
+for species co-occurrence in interaction networks. \emph{Theoretical
+Ecology}, 9, 39--48.
+
+\leavevmode\hypertarget{ref-Gonzalez-Varo2016LabLim}{}%
+Gonzalez-Varo, J.P. \& Traveset, A. (2016). The Labile Limits of
+Forbidden Interactions. \emph{Trends in Ecology \& Evolution}, 31,
+700--710.
+
+\leavevmode\hypertarget{ref-Jordano2003InvPro}{}%
+Jordano, P., Bascompte, J. \& Olesen, J.M. (2003). Invariant properties
+in coevolutionary networks of plantanimal interactions. \emph{Ecology
+Letters}, 6, 69--81.
+
 \leavevmode\hypertarget{ref-McLeod2020EffSpe}{}%
@@
 
+\leavevmode\hypertarget{ref-Olesen2010MisFor}{}%
+Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
+\& Jordano, P. (2010). Missing and forbidden links in mutualistic
+networks. \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 278, 725--732.
+
+\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
+Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
+The dissimilarity of species interaction networks. \emph{Ecology
+Letters}, 15, 1353--1361.
+
 \leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
@@
 \emph{Oikos}, 124, 243--251.
+
+\leavevmode\hypertarget{ref-Pulliam1974TheOpt}{}%
+Pulliam, H.R. (1974). On the Theory of Optimal Diets. \emph{The American
+Naturalist}, 108, 59--74.
+
+\leavevmode\hypertarget{ref-Strydom2022Food}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M.J., \emph{et al.} (2022). Food web reconstruction through phylogenetic
+transfer of low-rank network representation. \emph{Methods in Ecology
+and Evolution}, 13.
 

### 2023-01-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@9a4da8d988c19010dab17a231a563c4a46c68be4 🚀

@@
 representation of ecological networks, slowly moving from a binary to a
-probabilistic view of species interactions
-(\textbf{Poisot2016StrProa?}). This has several benefits. For example,
-probabilities represent the limit of our knowledge about species
-interactions and can indicate the expected frequency of two species
-interacting with each other {[}TK{]}. They are also very helpful in
-predictive models when modeling the spatial distribution of species
-(Cazelles \emph{et al.} 2016) and the temporal variability of ecological
-networks {[}TK{]}, generating new ecological data (e.g., Strydom
-\emph{et al.} 2022), and identifying priority sampling locations (see
-Andrade-Pacheco \emph{et al.} 2020 for an ecological example of a
-sampling optimization problem). Moreover, the high rate of false
-negatives in ecological network data, resulting from the difficulty of
-witnessing interactions between rare species, makes it hard to interpret
-non-observations of species interactions ecologically (Catchen \emph{et
-al.} 2023). Using probabilities instead of yes-no interactions accounts
-for these observation errors; in that case, only forbidden interactions
-(Jordano \emph{et al.} 2003; Olesen \emph{et al.} 2010) would have a
-probability value of zero (but see Gonzalez-Varo \& Traveset 2016).
+probabilistic view of species interactions (Poisot \emph{et al.} 2016).
+This has several benefits. For example, probabilities represent the
+limit of our knowledge about species interactions and can indicate the
+expected frequency of two species interacting with each other {[}TK{]}.
+They are also very helpful in predictive models when modeling the
+spatial distribution of species (Cazelles \emph{et al.} 2016) and the
+temporal variability of ecological networks {[}TK{]}, generating new
+ecological data (e.g., Strydom \emph{et al.} 2022), and identifying
+priority sampling locations (see Andrade-Pacheco \emph{et al.} 2020 for
+an ecological example of a sampling optimization problem). Moreover, the
+high rate of false negatives in ecological network data, resulting from
+the difficulty of witnessing interactions between rare species, makes it
+hard to interpret non-observations of species interactions ecologically
+(Catchen \emph{et al.} 2023). Using probabilities instead of yes-no
+interactions accounts for these observation errors; in that case, only
+forbidden interactions (Jordano \emph{et al.} 2003; Olesen \emph{et al.}
+2010) would have a probability value of zero (but see Gonzalez-Varo \&
+Traveset 2016).
 
@@
 
+\[P(i \rightarrow j)\]
+
 \begin{itemize}
@@
 networks}\label{probabilistic-local-networks}}
+
+\[P(i \rightarrow j | C, A, N, E, t)\]
+
+i = predator j = prey C = co-occurrence A = area N = relative abundance
+E = environment (including network) t = time
 
@@
 
+\leavevmode\hypertarget{ref-Poisot2016Structure}{}%
+Poisot, T., Cirtwill, A.R., Cazelles, K., Gravel, D., Fortin, M.-J. \&
+Stouffer, D.B. (2016). The structure of probabilistic networks.
+\emph{Methods in Ecology and Evolution}, 7, 303--312.
+
 \leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%

### 2023-01-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0d987a4a95a9b8ce4a7d52fcc44b70ecdcd52d81 🚀

@@
 \vfill
-
-        {\bfseries 1:}\,Community ecologists are increasingly thinking
-probabilistically when it comes to food webs and other ecological
-networks. Assuredly, the benefits of representing ecological
-interactions as probabilistic events (e.g., how likely are species to
-interact?) instead of binary objects (e.g., do species interact?) are
-numerous, from a better assessment of the spatiotemporal variation of
-trophic interactions to an increase capacity to reconstruct networks
-from sparse data. However, probabilities need to be used with caution
-when working with species interactions. Indeed, depending on the system
-at hand and the method used to build probabilistic networks,
-probabilities can have different interpretations that imply different
-ways to manipulate them. At the core of these differences lie the
-distinction between assessing the likelihood that two groups of
-individuals \emph{can} interact and the likelihood that they \emph{will}
-interact. This impacts the spatial, temporal, and taxonomic scaling of
-interaction probabilities, thus enlightening the need to properly define
-them in their ecological context. Published data on probabilistic
-species interactions are poorly documented in the literature, which
-impedes our ability to use them appropriately. With these challenges in
-mind, we propose a general approach to thinking about probabilities in
-regards to ecological interactions, with a strong focus on food webs,
-and call for better definitions and conceptualizations of probabilistic
-ecological networks, both at the local and regional scales.\\%
+Community ecologists are increasingly thinking probabilistically when it
+comes to food webs and other ecological networks. Assuredly, the
+benefits of representing ecological interactions as probabilistic events
+(e.g., how likely are species to interact?) instead of binary objects
+(e.g., do species interact?) are numerous, from a better assessment of
+the spatiotemporal variation of trophic interactions to an increase
+capacity to reconstruct networks from sparse data. However,
+probabilities need to be used with caution when working with species
+interactions. Indeed, depending on the system at hand and the method
+used to build probabilistic networks, probabilities can have different
+interpretations that imply different ways to manipulate them. At the
+core of these differences lie the distinction between assessing the
+likelihood that two groups of individuals \emph{can} interact and the
+likelihood that they \emph{will} interact. This impacts the spatial,
+temporal, and taxonomic scaling of interaction probabilities, thus
+enlightening the need to properly define them in their ecological
+context. Published data on probabilistic species interactions are poorly
+documented in the literature, which impedes our ability to use them
+appropriately. With these challenges in mind, we propose a general
+approach to thinking about probabilities in regards to ecological
+interactions, with a strong focus on food webs, and call for better
+definitions and conceptualizations of probabilistic ecological networks,
+both at the local and regional scales.
 

### 2023-01-28 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0d987a4a95a9b8ce4a7d52fcc44b70ecdcd52d81 🚀

@@
 
-        {\bfseries 1:}\,Community ecologists are increasingly thinking
-probabilistically when it comes to food webs and other ecological
-networks. Assuredly, the benefits of representing ecological
-interactions as probabilistic events (e.g., how likely are species to
-interact?) instead of binary objects (e.g., do species interact?) are
-numerous, from a better assessment of the spatiotemporal variation of
-trophic interactions to an increase capacity to reconstruct networks
-from sparse data. However, probabilities need to be used with caution
-when working with species interactions. Indeed, depending on the system
-at hand and the method used to build probabilistic networks,
-probabilities can have different interpretations that imply different
-ways to manipulate them. At the core of these differences lie the
-distinction between assessing the likelihood that two groups of
-individuals \emph{can} interact and the likelihood that they \emph{will}
-interact. This impacts the spatial, temporal, and taxonomic scaling of
-interaction probabilities, thus enlightening the need to properly define
-them in their ecological context. Published data on probabilistic
-species interactions are poorly documented in the literature, which
-impedes our ability to use them appropriately. With these challenges in
-mind, we propose a general approach to thinking about probabilities in
-regards to ecological interactions, with a strong focus on food webs,
-and call for better definitions and conceptualizations of probabilistic
-ecological networks, both at the local and regional scales.\\%
+Community ecologists are increasingly thinking probabilistically when it
+comes to food webs and other ecological networks. Assuredly, the
+benefits of representing ecological interactions as probabilistic events
+(e.g., how likely are species to interact?) instead of binary objects
+(e.g., do species interact?) are numerous, from a better assessment of
+the spatiotemporal variation of trophic interactions to an increase
+capacity to reconstruct networks from sparse data. However,
+probabilities need to be used with caution when working with species
+interactions. Indeed, depending on the system at hand and the method
+used to build probabilistic networks, probabilities can have different
+interpretations that imply different ways to manipulate them. At the
+core of these differences lie the distinction between assessing the
+likelihood that two groups of individuals \emph{can} interact and the
+likelihood that they \emph{will} interact. This impacts the spatial,
+temporal, and taxonomic scaling of interaction probabilities, thus
+enlightening the need to properly define them in their ecological
+context. Published data on probabilistic species interactions are poorly
+documented in the literature, which impedes our ability to use them
+appropriately. With these challenges in mind, we propose a general
+approach to thinking about probabilities in regards to ecological
+interactions, with a strong focus on food webs, and call for better
+definitions and conceptualizations of probabilistic ecological networks,
+both at the local and regional scales.
 

### 2023-02-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@5a85138104cfa2abd413f46f7fec3106326b9c3d 🚀

@@
 the core of this challenge lies the spatiotemporal variability of
-ecological networks (Poisot \emph{et al.} 2012, 2015), which makes
-documenting the location and timing of interactions difficult. Indeed,
-it is not sufficient to know if two species have the biological capacity
-to interact to infer the realization of their interaction at a specific
-time and space {[}TK{]}. Taking food webs as an example, a predator and
-its potential prey must first co-occur on the same territory in order
-for a trophic interaction to take place (Blanchet \emph{et al.} 2020).
-They must then encounter, which is conditional on their relative
-abundances in the ecosystem and the matching of their phenology (Poisot
-\emph{et al.} 2015). Finally, the interaction occurs only if the
-predators have a desire to consume their prey and are able to capture
-and ingest them (Pulliam 1974). Environmental (e.g.~temperature and
-presence of shelters) and biological (e.g.~physiological state of both
-species and availability of other prey species) factors contribute to
-this variability by impacting species co-occurrence {[}TK{]} and the
-realization of their interactions {[}TK{]}. In this context, it is
+ecological networks (\textbf{Poisot2012DisSpe?};
+\textbf{Poisot2015SpeWhy?}), which makes documenting the location and
+timing of interactions difficult. Indeed, it is not sufficient to know
+that two species have the biological capacity to interact to infer the
+realization of their interaction at a specific time and space (Dunne
+2006). Taking food webs as an example, a predator species and its
+potential prey must first co-occur on the same territory in order for a
+trophic interaction to take place (\textbf{Blanchet2020CooNot?}). They
+must then encounter, which is conditional on their relative abundances
+in the ecosystem and the matching of their phenology
+(\textbf{Poisot2015SpeWhy?}). Finally, the interaction occurs only if
+the predators have a desire to consume their prey and are able to
+capture and ingest them (\textbf{Pulliam1974TheOpt?}). Environmental
+(e.g.~temperature and presence of shelters) and biological
+(e.g.~physiological state of both species and availability of other prey
+species) factors contribute to this variability by impacting species
+co-occurrence (Araujo \emph{et al.} 2011) and the realization of their
+interactions (\textbf{Poisot2015SpeWhy?}). In this context, it is
 unsurprising that computational methods are being developed in ecology
 to help alleviate the colossal sampling efforts required to document
-species interactions across time and space (Strydom \emph{et al.} 2021).
-Having a better portrait of species interactions and the emerging
-structure of food webs is important since it lays the groundwork for
-understanding the functioning {[}TK{]}, dynamics {[}TK{]}, and
-resilience {[}TK{]} of ecosystems worldwide.
+species interactions across time and space
+(\textbf{Strydom2021RoaPre?}). Having a better portrait of species
+interactions and the emerging structure of their food webs is important
+since it lays the groundwork for understanding the functioning,
+dynamics, and resilience of ecosystems worldwide (e.g., Proulx \emph{et
+al.} 2005; Pascual \emph{et al.} 2006; Delmas \emph{et al.} 2019).
 
-The recognition of the variability of species interactions and the
-emergence of numerical methods have led ecologists to rethink their
+The recognition of the intrinsic variability of species interactions and
+the emergence of numerical methods have led ecologists to rethink their
 representation of ecological networks, slowly moving from a binary to a
@@
 This has several benefits. For example, probabilities represent the
-limit of our knowledge about species interactions and can indicate the
-expected frequency of two species interacting with each other {[}TK{]}.
-They are also very helpful in predictive models when modeling the
-spatial distribution of species (Cazelles \emph{et al.} 2016) and the
-temporal variability of ecological networks {[}TK{]}, generating new
+limit of our knowledge about species interactions and can inform us
+about the expected number of interactions and emerging network
+properties despite this limited knowledge (Poisot \emph{et al.} 2016).
+They are also very helpful in predicting the spatial distribution of
+species within networks (\textbf{Cazelles2016TheSpe?}) and the temporal
+variability of interactions (Poisot \emph{et al.} 2015), generating new
 ecological data (e.g., Strydom \emph{et al.} 2022), and identifying
-priority sampling locations (see Andrade-Pacheco \emph{et al.} 2020 for
-an ecological example of a sampling optimization problem). Moreover, the
-high rate of false negatives in ecological network data, resulting from
-the difficulty of witnessing interactions between rare species, makes it
-hard to interpret non-observations of species interactions ecologically
-(Catchen \emph{et al.} 2023). Using probabilities instead of yes-no
+priority sampling locations of species interactions (see
+\textbf{Andrade-Pacheco2020FinHot?} for an ecological example of a
+sampling optimization problem). Moreover, the high rate of false
+negatives in ecological network data, resulting from the difficulty of
+witnessing interactions between rare species, makes it hard to interpret
+non-observations of species interactions ecologically
+(\textbf{Catchen2023MisLin?}). Using probabilities instead of yes-no
 interactions accounts for these observation errors; in that case, only
-forbidden interactions (Jordano \emph{et al.} 2003; Olesen \emph{et al.}
-2010) would have a probability value of zero (but see Gonzalez-Varo \&
-Traveset 2016).
+forbidden interactions (\textbf{Jordano2003InvPro?};
+\textbf{Olesen2010MisFor?}) would have a probability value of zero (but
+see \textbf{Gonzalez-Varo2016LabLim?}). Many measures have been
+developed to describe the structure (Poisot \emph{et al.} 2016) and
+diversity (Ohlmann \emph{et al.} 2019; Godsoe \emph{et al.} n.d.) of
+probabilistic interactions, which shows the potential of this framework
+in the study of a variety of ecological phenomena.
 
@@
 
+Papers: Guimarães (2020)
+
 \hypertarget{probabilistic-metawebs}{%
@@
 
-i = predator j = prey C = co-occurrence A = area N = relative abundance
-E = environment (including network) t = time
+i = predator j = prey C = co-occurrence (and relative abundance?) A =
+area N = relative abundance (or network?) E = environment (including
+network?) t = time
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Andrade-Pacheco2020FinHot}{}%
-Andrade-Pacheco, R., Rerolle, F., Lemoine, J., Hernandez, L., Meïté, A.,
-Juziwelo, L., \emph{et al.} (2020). Finding hotspots: Development of an
-adaptive spatial sampling approach. \emph{Scientific Reports}, 10,
-10939.
+\leavevmode\hypertarget{ref-Araujo2011UsiSpe}{}%
+Araujo, M.B., Rozenfeld, A., Rahbek, C. \& Marquet, P.A. (2011). Using
+species co-occurrence networks to assess the impacts of climate change.
+\emph{Ecography}, 34, 897--908.
 
-\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
-Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
-evidence of ecological interactions. \emph{Ecology Letters}, 23,
-1050--1063.
+\leavevmode\hypertarget{ref-Delmas2019AnaEco}{}%
+Delmas, E., Besson, M., Brice, M.-H., Burkle, L.A., Dalla Riva, G.V.,
+Fortin, M.-J., \emph{et al.} (2019). Analysing ecological networks of
+species interactions. \emph{Biological Reviews}, 94, 16--36.
 
-\leavevmode\hypertarget{ref-Catchen2023MisLin}{}%
-Catchen, M.D., Poisot, T., Pollock, L.J. \& Gonzalez, A. (2023). The
-missing link: Discerning true from false negatives when sampling species
-interaction networks.
+\leavevmode\hypertarget{ref-Dunne2006Network}{}%
+Dunne, J.A. (2006). The Network Structure of Food Webs. In:
+\emph{Ecological networks: Linking structure and dynamics} (eds. Dunne,
+J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
 
-\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
-Cazelles, K., Araujo, M.B., Mouquet, N. \& Gravel, D. (2016). A theory
-for species co-occurrence in interaction networks. \emph{Theoretical
-Ecology}, 9, 39--48.
+\leavevmode\hypertarget{ref-GodsoeSpeInt}{}%
+Godsoe, W., Murray, R. \& Iritani, R. (n.d.). Species interactions and
+diversity: A unified framework using Hill numbers. \emph{Oikos}, n/a,
+e09282.
 
-\leavevmode\hypertarget{ref-Gonzalez-Varo2016LabLim}{}%
-Gonzalez-Varo, J.P. \& Traveset, A. (2016). The Labile Limits of
-Forbidden Interactions. \emph{Trends in Ecology \& Evolution}, 31,
-700--710.
-
-\leavevmode\hypertarget{ref-Jordano2003InvPro}{}%
-Jordano, P., Bascompte, J. \& Olesen, J.M. (2003). Invariant properties
-in coevolutionary networks of plantanimal interactions. \emph{Ecology
-Letters}, 6, 69--81.
+\leavevmode\hypertarget{ref-Guimaraes2020StrEco}{}%
+Guimarães, P.R. (2020). The Structure of Ecological Networks Across
+Levels of Organization. \emph{Annual Review of Ecology, Evolution, and
+Systematics}, 51, 433--460.
 
@@
 
-\leavevmode\hypertarget{ref-Olesen2010MisFor}{}%
-Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
-\& Jordano, P. (2010). Missing and forbidden links in mutualistic
-networks. \emph{Proceedings of the Royal Society B: Biological
-Sciences}, 278, 725--732.
+\leavevmode\hypertarget{ref-Ohlmann2019DivInd}{}%
+Ohlmann, M., Miele, V., Dray, S., Chalmandrier, L., O'Connor, L. \&
+Thuiller, W. (2019). Diversity indices for ecological networks: A
+unifying framework using Hill numbers. \emph{Ecology Letters}, 22,
+737--747.
 
-\leavevmode\hypertarget{ref-Poisot2012DisSpe}{}%
-Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
-The dissimilarity of species interaction networks. \emph{Ecology
-Letters}, 15, 1353--1361.
+\leavevmode\hypertarget{ref-Pascual2006EcoNet}{}%
+Pascual, M., Dunne, J.A. \& Dunne, J.A. (2006). \emph{Ecological
+Networks: Linking Structure to Dynamics in Food Webs}. Oxford University
+Press, USA.
 
@@
 
-\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+\leavevmode\hypertarget{ref-Poisot2015Speciesa}{}%
 Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
@@
 
-\leavevmode\hypertarget{ref-Pulliam1974TheOpt}{}%
-Pulliam, H.R. (1974). On the Theory of Optimal Diets. \emph{The American
-Naturalist}, 108, 59--74.
+\leavevmode\hypertarget{ref-Proulx2005NetThi}{}%
+Proulx, S.R., Promislow, D.E.L. \& Phillips, P.C. (2005). Network
+thinking in ecology and evolution. \emph{Trends in Ecology \&
+Evolution}, SPECIAL issue: BUMPER book REVIEW, 20, 345--353.
 
@@
 
-\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
-Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
-predicting species interaction networks (across space and time).
-\emph{Philosophical Transactions of the Royal Society B-Biological
-Sciences}, 376, 20210063.
-
 \end{CSLReferences}

### 2023-02-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@1c122f954c03d81853ba457abc14ae434005d61d 🚀

@@
 
+\hypertarget{acknowledgement}{%
+\section{Acknowledgement}\label{acknowledgement}}
+
+We acknowledge that this study was conducted on land within the
+traditional unceded territory of the Saint Lawrence Iroquoian,
+Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. This
+work was supported by the Institute for Data Valorisation (IVADO) and
+the Natural Sciences and Engineering Research Council of Canada (NSERC)
+Collaborative Research and Training Experience (CREATE) program, through
+the Computational Biodiversity Science and Services (BIOS²) program. A
+special thank to all members of the Black Holes and Revelations working
+group (organized by BIOS²) for their insightful discussions and valuable
+feedbacks on this manuscript.
+
 \hypertarget{references}{%

### 2023-02-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@2c56085dbe296d98270202ca1acb3669231eb772 🚀

@@
 
-\hypertarget{overview-of-interaction-probabilities}{%
-\subsection{Overview of interaction
-probabilities}\label{overview-of-interaction-probabilities}}
+The basic unit of food webs and other ecological networks are
+individuals that interact with each others (e.g., by predation; Elton
+2001). The aggregation of these individuals into more or less
+homogeneous groups (e.g., populations, species, trophic species) allows
+us to represent networks at different scales, which impacts the
+properties and behaviour of these systems (Guimarães 2020). A network's
+nodes can thus designate distinct levels of organization, whereas the
+edges linking these nodes can describe a variety of interaction
+measures. When using a Boolean (yes-no) representation of biotic
+interactions, the observation that one individual from group (or node)
+\(i\) interacts with another individual from group \(j\) is enough to
+set the interaction \(A_{i,j}\) to 1. This simplified representation of
+food webs is a highly valuable source of ecological information (Pascual
+\emph{et al.} 2006) even though it overlooks important factors regarding
+interaction strengths. These, in turn, can be represented using weighted
+interactions, which better describe the energy flows, demographic
+impacts or frequencies of interactions between nodes (Berlow \emph{et
+al.} 2004; Borrett \& Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or
+\(\mathbb{R}\) depending on the measure. For example, they can be used
+to estimate the average number of prey individuals consumed by the
+predators in a given time period. This extra amount of ecological
+information typically comes at a cost of greater sampling effort or data
+requirement in predictive models (Strydom \emph{et al.} 2021), which can
+lead to high uncertainties when building these types of networks.
 
-How are interaction probabilities defined in the literature? It might
-not be as intuitive as one would think.
+The uncertainty and spatiotemporal variability of both types of biotic
+interactions (Boolean and weighted) can be represented
+probabilistically. On one hand, Boolean interactions follow a Bernoulli
+distribution \(A_{i,j} \sim {\rm Bernoulli}(p)\), with \(p\) being the
+probability of interactions. The only two possible outcomes are the
+presence (\(A_{i,j} = 1\)) or absence (\(A_{i,j} = 0\)) of an
+interaction between the two nodes. Weighted interactions, on the other
+hand, can follow various probability distributions depending on the
+measure used. In this case, the event's outcome is the value of
+interaction strength. For instance, weights can follow a Poisson
+distribution \(A_{i,j} \sim {\rm Poisson}(\lambda)\) when predicting
+frequencies of interactions between pairs of nodes, with \(\lambda\)
+being the expected rate of interaction. The definition and
+interpretation of parameters like \(p\) and \(\lambda\) are inextricably
+linked to environmental and biological factors such as species relative
+abundance, traits, area, and time, depending on the type of interaction.
+Because Boolean species interactions are much more documented in the
+literature, our primary focus in this contribution will be on addressing
+the challenges in defining and interpretating \(p\) for pairwise species
+interactions.
 
-\begin{itemize}
-\tightlist
-\item
-  There is a big difference in how we interpret the probability that two
-  species \emph{can} interact (metaweb) and the probability that they
-  \emph{will} interact (realized networks).
-\item
-  Interaction probabilities can be used to describe Boolean interactions
-  (e.g., the probability that two species interact) and weighted
-  interactions (e.g., the probability distribution of the amount of
-  energy flow between two species).
-\item
-  In many studies, it is not obvious if authors use interaction scores
-  or probabilities (in the latter case, it is rarely specified what
-  these probabilities truly represent).
-\end{itemize}
-
-Papers: Guimarães (2020)
+The first aspect to take into consideration when estimating or using
+probabilities of interactions is knowing if they describe the likelihood
+of potential or realized interactions. A potential interaction is
+defined as the biological capacity of two species to interact (i.e., the
+probability that they \emph{can} interact) whereas a realized
+interaction refers to the materialization or observation of this
+interaction in a delineated space and time period (i.e., the probability
+that they \emph{will} interact). Here, we will use the terms
+\emph{metaweb} to designate networks of potential interactions and
+\emph{local networks} for those of realized interactions. Frequent
+confusion arises among ecologists over the use of these two terms,
+especially in a probabilistic context. Indeed, in many studies of
+probabilistic ecological networks, it remains unclear when authors
+describe potential or realized interactions, or when so-called
+probabilities are actually \emph{interaction scores}. A better
+understanding of these differences would alleviate interpretation errors
+and help ecologists use these numbers more appropriately.
 
@@
   probabilistic and intuitive?
+\item
+  Low probability with rare interactions?
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-Berlow2004IntStr}{}%
+Berlow, E.L., Neutel, A.-M., Cohen, J.E., De Ruiter, P.C., Ebenman, B.,
+Emmerson, M., \emph{et al.} (2004). Interaction strengths in food webs:
+Issues and opportunities. \emph{Journal of Animal Ecology}, 73,
+585--598.
+
+\leavevmode\hypertarget{ref-Borrett2019WalPar}{}%
+Borrett, S.R. \& Scharler, U.M. (2019). Walk partitions of flow in
+Ecological Network Analysis: Review and synthesis of methods and
+indicators. \emph{Ecological Indicators}, 106, 105451.
+
 \leavevmode\hypertarget{ref-Delmas2019AnaEco}{}%
@@
 J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
+
+\leavevmode\hypertarget{ref-Elton2001AniEco}{}%
+Elton, C.S. (2001). \emph{Animal Ecology}. University of Chicago Press,
+Chicago, IL.
 
@@
 
+\leavevmode\hypertarget{ref-Strydom2021Roadmapa}{}%
+Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
+predicting species interaction networks (across space and time).
+\emph{Philosophical Transactions of the Royal Society B-Biological
+Sciences}, 376, 20210063.
+
 \end{CSLReferences}

### 2023-02-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@c9e3dd5b428ea22dc5ecfea7425b6f717e3897de 🚀

@@
 the core of this challenge lies the spatiotemporal variability of
-ecological networks (\textbf{Poisot2012DisSpe?};
-\textbf{Poisot2015SpeWhy?}), which makes documenting the location and
-timing of interactions difficult. Indeed, it is not sufficient to know
-that two species have the biological capacity to interact to infer the
-realization of their interaction at a specific time and space (Dunne
-2006). Taking food webs as an example, a predator species and its
-potential prey must first co-occur on the same territory in order for a
-trophic interaction to take place (\textbf{Blanchet2020CooNot?}). They
-must then encounter, which is conditional on their relative abundances
-in the ecosystem and the matching of their phenology
-(\textbf{Poisot2015SpeWhy?}). Finally, the interaction occurs only if
-the predators have a desire to consume their prey and are able to
-capture and ingest them (\textbf{Pulliam1974TheOpt?}). Environmental
+ecological networks (Poisot \emph{et al.} 2012, 2015), which makes
+documenting the location and timing of interactions difficult. Indeed,
+it is not sufficient to know that two species have the biological
+capacity to interact to infer the realization of their interaction at a
+specific time and space (Dunne 2006). Taking food webs as an example, a
+predator species and its potential prey must first co-occur on the same
+territory in order for a trophic interaction to take place (Blanchet
+\emph{et al.} 2020). They must then encounter, which is conditional on
+their relative abundances in the ecosystem and the matching of their
+phenology (Poisot \emph{et al.} 2015). Finally, the interaction occurs
+only if the predators have a desire to consume their prey and are able
+to capture and ingest them (Pulliam 1974). Environmental
 (e.g.~temperature and presence of shelters) and biological
@@
 co-occurrence (Araujo \emph{et al.} 2011) and the realization of their
-interactions (\textbf{Poisot2015SpeWhy?}). In this context, it is
+interactions (Poisot \emph{et al.} 2015). In this context, it is
 unsurprising that computational methods are being developed in ecology
 to help alleviate the colossal sampling efforts required to document
-species interactions across time and space
-(\textbf{Strydom2021RoaPre?}). Having a better portrait of species
-interactions and the emerging structure of their food webs is important
-since it lays the groundwork for understanding the functioning,
-dynamics, and resilience of ecosystems worldwide (e.g., Proulx \emph{et
-al.} 2005; Pascual \emph{et al.} 2006; Delmas \emph{et al.} 2019).
+species interactions across time and space (Strydom \emph{et al.} 2021).
+Having a better portrait of species interactions and the emerging
+structure of their food webs is important since it lays the groundwork
+for understanding the functioning, dynamics, and resilience of
+ecosystems worldwide (e.g., Proulx \emph{et al.} 2005; Pascual \emph{et
+al.} 2006; Delmas \emph{et al.} 2019).
 
@@
 They are also very helpful in predicting the spatial distribution of
-species within networks (\textbf{Cazelles2016TheSpe?}) and the temporal
+species within networks (Cazelles \emph{et al.} 2016) and the temporal
 variability of interactions (Poisot \emph{et al.} 2015), generating new
 ecological data (e.g., Strydom \emph{et al.} 2022), and identifying
-priority sampling locations of species interactions (see
-\textbf{Andrade-Pacheco2020FinHot?} for an ecological example of a
-sampling optimization problem). Moreover, the high rate of false
-negatives in ecological network data, resulting from the difficulty of
-witnessing interactions between rare species, makes it hard to interpret
-non-observations of species interactions ecologically
-(\textbf{Catchen2023MisLin?}). Using probabilities instead of yes-no
-interactions accounts for these observation errors; in that case, only
-forbidden interactions (\textbf{Jordano2003InvPro?};
-\textbf{Olesen2010MisFor?}) would have a probability value of zero (but
-see \textbf{Gonzalez-Varo2016LabLim?}). Many measures have been
-developed to describe the structure (Poisot \emph{et al.} 2016) and
-diversity (Ohlmann \emph{et al.} 2019; Godsoe \emph{et al.} n.d.) of
-probabilistic interactions, which shows the potential of this framework
-in the study of a variety of ecological phenomena.
+priority sampling locations of species interactions (see Andrade-Pacheco
+\emph{et al.} 2020 for an ecological example of a sampling optimization
+problem). Moreover, the high rate of false negatives in ecological
+network data, resulting from the difficulty of witnessing interactions
+between rare species, makes it hard to interpret non-observations of
+species interactions ecologically (Catchen \emph{et al.} 2023). Using
+probabilities instead of yes-no interactions accounts for these
+observation errors; in that case, only forbidden interactions (Jordano
+\emph{et al.} 2003; Olesen \emph{et al.} 2010) would have a probability
+value of zero (but see Gonzalez-Varo \& Traveset 2016). Many measures
+have been developed to describe the structure (Poisot \emph{et al.}
+2016) and diversity (Ohlmann \emph{et al.} 2019; \textbf{GodsoeSpeInt?})
+of probabilistic interactions, which shows the potential of this
+framework in the study of a variety of ecological phenomena.
 
@@
 
-\textbf{Papers:} (\textbf{Strydom2022FooWeb?})
+\textbf{Papers:} Strydom \emph{et al.} (2022)
 
@@
 \textbf{Papers:} there might be something in these McLeod \emph{et al.}
-(2020); (\textbf{McLeod2021SamAsy?}); (\textbf{Wood2015EffSpa?})
+(2020); McLeod \emph{et al.} (2021); Wood \emph{et al.} (2015)
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Andrade-Pacheco2020Finding}{}%
+Andrade-Pacheco, R., Rerolle, F., Lemoine, J., Hernandez, L., Meïté, A.,
+Juziwelo, L., \emph{et al.} (2020). Finding hotspots: Development of an
+adaptive spatial sampling approach. \emph{Scientific Reports}, 10,
+10939.
+
 \leavevmode\hypertarget{ref-Araujo2011UsiSpe}{}%
@@
 
+\leavevmode\hypertarget{ref-Blanchet2020Cooccurrencea}{}%
+Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
+evidence of ecological interactions. \emph{Ecology Letters}, 23,
+1050--1063.
+
 \leavevmode\hypertarget{ref-Borrett2019WalPar}{}%
@@
 indicators. \emph{Ecological Indicators}, 106, 105451.
+
+\leavevmode\hypertarget{ref-Catchen2023Missinga}{}%
+Catchen, M.D., Poisot, T., Pollock, L.J. \& Gonzalez, A. (2023). The
+missing link: Discerning true from false negatives when sampling species
+interaction networks.
+
+\leavevmode\hypertarget{ref-Cazelles2016Theorya}{}%
+Cazelles, K., Araujo, M.B., Mouquet, N. \& Gravel, D. (2016). A theory
+for species co-occurrence in interaction networks. \emph{Theoretical
+Ecology}, 9, 39--48.
 
@@
 
-\leavevmode\hypertarget{ref-GodsoeSpeInt}{}%
-Godsoe, W., Murray, R. \& Iritani, R. (n.d.). Species interactions and
-diversity: A unified framework using Hill numbers. \emph{Oikos}, n/a,
-e09282.
+\leavevmode\hypertarget{ref-Gonzalez-Varo2016Labilea}{}%
+Gonzalez-Varo, J.P. \& Traveset, A. (2016). The Labile Limits of
+Forbidden Interactions. \emph{Trends in Ecology \& Evolution}, 31,
+700--710.
 
@@
 Systematics}, 51, 433--460.
+
+\leavevmode\hypertarget{ref-Jordano2003Invarianta}{}%
+Jordano, P., Bascompte, J. \& Olesen, J.M. (2003). Invariant properties
+in coevolutionary networks of plantanimal interactions. \emph{Ecology
+Letters}, 6, 69--81.
+
+\leavevmode\hypertarget{ref-McLeod2021Sampling}{}%
+McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
+M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
+of spatial multi-trophic networks. \emph{Oikos}, n/a.
 
@@
 
+\leavevmode\hypertarget{ref-Olesen2010Missing}{}%
+Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
+\& Jordano, P. (2010). Missing and forbidden links in mutualistic
+networks. \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 278, 725--732.
+
 \leavevmode\hypertarget{ref-Pascual2006EcoNet}{}%
@@
 Press, USA.
+
+\leavevmode\hypertarget{ref-Poisot2012Dissimilaritya}{}%
+Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel, D. (2012).
+The dissimilarity of species interaction networks. \emph{Ecology
+Letters}, 15, 1353--1361.
 
@@
 
+\leavevmode\hypertarget{ref-Pulliam1974Theory}{}%
+Pulliam, H.R. (1974). On the Theory of Optimal Diets. \emph{The American
+Naturalist}, 108, 59--74.
+
 \leavevmode\hypertarget{ref-Strydom2022Food}{}%
@@
 
+\leavevmode\hypertarget{ref-Wood2015Effects}{}%
+Wood, S.A., Russell, R., Hanson, D., Williams, R.J. \& Dunne, J.A.
+(2015). Effects of spatial scale of sampling on food web structure.
+\emph{Ecology and Evolution}, 5, 3769--3782.
+
 \end{CSLReferences}

### 2023-02-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@735e160b89cdc3415715bdb67c52f2cafe419e94 🚀

@@
 only if the predators have a desire to consume their prey and are able
-to capture and ingest them (Pulliam 1974). Environmental
-(e.g.~temperature and presence of shelters) and biological
-(e.g.~physiological state of both species and availability of other prey
-species) factors contribute to this variability by impacting species
-co-occurrence (Araujo \emph{et al.} 2011) and the realization of their
-interactions (Poisot \emph{et al.} 2015). In this context, it is
-unsurprising that computational methods are being developed in ecology
-to help alleviate the colossal sampling efforts required to document
-species interactions across time and space (Strydom \emph{et al.} 2021).
-Having a better portrait of species interactions and the emerging
-structure of their food webs is important since it lays the groundwork
-for understanding the functioning, dynamics, and resilience of
-ecosystems worldwide (e.g., Proulx \emph{et al.} 2005; Pascual \emph{et
-al.} 2006; Delmas \emph{et al.} 2019).
+to capture and ingest them (Pulliam 1974). Environmental (e.g.
+temperature and presence of shelters) and biological (e.g.~physiological
+state of both species and availability of other prey species) factors
+contribute to this variability by impacting species co-occurrence
+(Araujo \emph{et al.} 2011) and the realization of their interactions
+(Poisot \emph{et al.} 2015). In this context, the development of
+computational methods in ecology can help alleviate the colossal
+sampling efforts required to document species interactions across time
+and space (Strydom \emph{et al.} 2021). Having a better portrait of
+species interactions and the emerging structure of their food webs is
+important since it lays the groundwork for understanding the
+functioning, dynamics, and resilience of ecosystems worldwide (e.g.,
+Proulx \emph{et al.} 2005; Pascual \emph{et al.} 2006; Delmas \emph{et
+al.} 2019).
 
@@
 have been developed to describe the structure (Poisot \emph{et al.}
-2016) and diversity (Ohlmann \emph{et al.} 2019; \textbf{GodsoeSpeInt?})
-of probabilistic interactions, which shows the potential of this
+2016) and diversity (Ohlmann \emph{et al.} 2019; Godsoe \emph{et al.}
+2022) of probabilistic interactions, which shows the potential of this
 framework in the study of a variety of ecological phenomena.
@@
 
+\hypertarget{food-web-representations}{%
+\subsection{Food-web representations}\label{food-web-representations}}
+
 The basic unit of food webs and other ecological networks are
 individuals that interact with each others (e.g., by predation; Elton
-2001). The aggregation of these individuals into more or less
-homogeneous groups (e.g., populations, species, trophic species) allows
-us to represent networks at different scales, which impacts the
-properties and behaviour of these systems (Guimarães 2020). A network's
-nodes can thus designate distinct levels of organization, whereas the
-edges linking these nodes can describe a variety of interaction
-measures. When using a Boolean (yes-no) representation of biotic
-interactions, the observation that one individual from group (or node)
-\(i\) interacts with another individual from group \(j\) is enough to
-set the interaction \(A_{i,j}\) to 1. This simplified representation of
-food webs is a highly valuable source of ecological information (Pascual
-\emph{et al.} 2006) even though it overlooks important factors regarding
-interaction strengths. These, in turn, can be represented using weighted
-interactions, which better describe the energy flows, demographic
-impacts or frequencies of interactions between nodes (Berlow \emph{et
-al.} 2004; Borrett \& Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or
-\(\mathbb{R}\) depending on the measure. For example, they can be used
-to estimate the average number of prey individuals consumed by the
-predators in a given time period. This extra amount of ecological
-information typically comes at a cost of greater sampling effort or data
-requirement in predictive models (Strydom \emph{et al.} 2021), which can
-lead to high uncertainties when building these types of networks.
+2001), forming individual-based networks. The aggregation of these
+individuals into more or less homogeneous groups (e.g., populations,
+species, trophic species, families) allows us to represent networks at
+broader scales, which impacts the properties and behaviour of these
+systems (Guimarães 2020). A network's nodes can thus designate distinct
+levels of organization, whereas the edges linking these nodes can
+describe a variety of interaction measures. When using a Boolean
+(yes-no) representation of biotic interactions, the observation that one
+individual from group (or node) \(i\) interacts with another individual
+from group \(j\) is enough to set the interaction \(A_{i,j}\) to 1. This
+simplified representation of food webs is a highly valuable source of
+ecological information (Pascual \emph{et al.} 2006) even though it
+overlooks important factors regarding interaction strengths. These, in
+turn, can be represented using weighted interactions, which better
+describe the energy flows, demographic impacts or frequencies of
+interactions between nodes (Berlow \emph{et al.} 2004; Borrett \&
+Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\)
+depending on the measure. For example, they can be used to estimate the
+average number of prey individuals consumed by the predators in a given
+time period. This extra amount of ecological information typically comes
+at a cost of greater sampling effort or data requirement in predictive
+models (Strydom \emph{et al.} 2021), which can lead to high
+uncertainties when building these types of networks. Therefore,
+important methodological and conceptual decisions must been made when
+sampling and building food webs.
 
-The uncertainty and spatiotemporal variability of both types of biotic
+The uncertainty and spatiotemporal variability of both types of trophic
 interactions (Boolean and weighted) can be represented
@@
 interaction in a delineated space and time period (i.e., the probability
-that they \emph{will} interact). Here, we will use the terms
-\emph{metaweb} to designate networks of potential interactions and
-\emph{local networks} for those of realized interactions. Frequent
-confusion arises among ecologists over the use of these two terms,
-especially in a probabilistic context. Indeed, in many studies of
-probabilistic ecological networks, it remains unclear when authors
-describe potential or realized interactions, or when so-called
-probabilities are actually \emph{interaction scores}. A better
-understanding of these differences would alleviate interpretation errors
-and help ecologists use these numbers more appropriately.
+that they interact). Here, we will use the terms \emph{metaweb} to
+designate networks of potential interactions and \emph{local networks}
+for those of realized interactions. Frequent confusion arises among
+ecologists over the use of these two terms, especially in a
+probabilistic context. Indeed, in many studies of probabilistic
+ecological networks, it remains unclear when authors describe potential
+or realized interactions, or when so-called probabilities are actually
+\emph{interaction scores}. A better understanding of these differences
+would alleviate interpretation errors and help ecologists use these
+numbers more appropriately.
 
@@
 
-What does a probability in the context of a metaweb mean?
+Metawebs are networks of potential interactions, representing the
+probability that two taxa can interact regardless of biological
+plasticity, environmental variability or co-occurrence. They are the
+network analogue to the species pool, where local networks originate
+from a subset of both species (nodes) and interactions (edges). For this
+reason, they have been initially designed for broad spatial, temporal,
+and taxonomic scales (e.g, species food webs at the continental scale).
+However, in the next section, we argue that this concept can also be
+used at smaller scales, with similar ecological meaning.
 
-\[P(i \rightarrow j)\]
+We can express the probability that two taxa \(i\) and \(j\) can
+interact as
 
-\begin{itemize}
-\tightlist
-\item
-  It means the probability that two taxa can interact, regardless of
-  biological plasticity, environmental variability, or co-occurrence.
-\item
-  One observation is enough to set this probability to one.
-\item
-  Can we turn this into a local network realisation that is also
-  probabilistic and intuitive?
-\item
-  Low probability with rare interactions?
-\end{itemize}
+\begin{equation}\protect\hypertarget{eq:metaweb}{}{P(i \rightarrow j),}\label{eq:metaweb}\end{equation}
 
-\textbf{Papers:} Strydom \emph{et al.} (2022)
+which is context independent. In other words, the probability that two
+species can interact is not contingent on location, time, and
+environmental factors. Nevertheless, one aspect of a metaweb that could
+be conditional on these factors is the list of species (or taxa) it is
+built from when assembled for a specific region.
+
+Starting from a selected set of species, metawebs can be built using
+different data sources, including literature review, field work, and
+predictive models (e.g., the metaweb of Canadian mammals inferred by
+Strydom \emph{et al.} 2022). Every pair of species that has been
+observed to interact at least once can be given a probability of
+interaction of \(1\); we know that they \emph{can} interact. This means
+that rare interactions can be given high probabilities in the metaweb.
+Unobserved interactions, on the other hand, are given lower
+probabilities, going as low as \(0\) for forbidden links. Two important
+nuances must however be made here. Because of observation errors due to
+taxonomic misidentifications and ecological misinterpretations, many
+observations of interactions are actually false positives. Similarly,
+forbidden interactions can be false negatives if e.g.~they have been
+assessed for specific phenotypes, locations or time. Implementing a
+Bayesian framework, which updates prior probabilities of interactions
+with empirical data, could lessen these errors.
+
+One potential application of metawebs is the prediction of networks of
+realized interactions. Even though the spatiotemporal variation of
+interactions is not considered in metawebs, they can nevertheless be a
+useful tool to reconstruct local networks. First, metawebs set the upper
+limit of species interactions, i.e.~the probability that two species
+interact at a specific location is always lower than the probability of
+their potential interaction
+(\(P(i \rightarrow j) < P(i \rightarrow j | x_1, x_2, ...)\)). This
+implies that predicting local networks from metawebs realistically might
+need be done by filtering out interactions from its subnetworks. Second,
+the structure of local networks is constrained by the one of their
+metaweb. Inferring their structure from the metaweb first could help
+predicting which potential interactions are not realized. Ultimately, we
+believe that predicting probabilistic local networks from metawebs must
+be done with caution, as long as uncertainty is adequately propagated.
 
@@
 
+\leavevmode\hypertarget{ref-Godsoe2022SpeInt}{}%
+Godsoe, W., Murray, R. \& Iritani, R. (2022). Species interactions and
+diversity: A unified framework using Hill numbers. \emph{Oikos}, n/a,
+e09282.
+
 \leavevmode\hypertarget{ref-Gonzalez-Varo2016Labilea}{}%

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@55e45e6fe79c220764120a9d273be381050b76e1 🚀

@@
 specific time and space (Dunne 2006). Taking food webs as an example, a
-predator species and its potential prey must first co-occur on the same
-territory in order for a trophic interaction to take place (Blanchet
-\emph{et al.} 2020). They must then encounter, which is conditional on
-their relative abundances in the ecosystem and the matching of their
-phenology (Poisot \emph{et al.} 2015). Finally, the interaction occurs
-only if the predators have a desire to consume their prey and are able
-to capture and ingest them (Pulliam 1974). Environmental (e.g.
-temperature and presence of shelters) and biological (e.g.~physiological
-state of both species and availability of other prey species) factors
-contribute to this variability by impacting species co-occurrence
-(Araujo \emph{et al.} 2011) and the realization of their interactions
-(Poisot \emph{et al.} 2015). In this context, the development of
-computational methods in ecology can help alleviate the colossal
-sampling efforts required to document species interactions across time
-and space (Strydom \emph{et al.} 2021). Having a better portrait of
-species interactions and the emerging structure of their food webs is
-important since it lays the groundwork for understanding the
-functioning, dynamics, and resilience of ecosystems worldwide (e.g.,
-Proulx \emph{et al.} 2005; Pascual \emph{et al.} 2006; Delmas \emph{et
-al.} 2019).
+predator species and its potential prey must first co-occur in order for
+a trophic interaction to take place (Blanchet \emph{et al.} 2020). They
+must then encounter, which is conditional on their relative abundances
+in the ecosystem and the matching of their phenology (Poisot \emph{et
+al.} 2015). Finally, the interaction occurs only if the predators have a
+desire to consume their prey and are able to capture and ingest them
+(Pulliam 1974). Environmental (e.g.~temperature and presence of
+shelters) and biological (e.g.~physiological state of both species and
+availability of other prey species) factors contribute to this
+variability by impacting species co-occurrence (Araujo \emph{et al.}
+2011) and the realization of their interactions (Poisot \emph{et al.}
+2015). In this context, the development of computational methods in
+ecology can help alleviate the colossal sampling efforts required to
+document species interactions across time and space (Strydom \emph{et
+al.} 2021). Having a better portrait of species interactions and the
+emerging structure of their food webs is important since it lays the
+groundwork for understanding the functioning, dynamics, and resilience
+of ecosystems worldwide (e.g., Proulx \emph{et al.} 2005; Pascual
+\emph{et al.} 2006; Delmas \emph{et al.} 2019).
 
@@
 
-The first aspect to take into consideration when estimating or using
-probabilities of interactions is knowing if they describe the likelihood
-of potential or realized interactions. A potential interaction is
-defined as the biological capacity of two species to interact (i.e., the
-probability that they \emph{can} interact) whereas a realized
-interaction refers to the materialization or observation of this
-interaction in a delineated space and time period (i.e., the probability
-that they interact). Here, we will use the terms \emph{metaweb} to
-designate networks of potential interactions and \emph{local networks}
-for those of realized interactions. Frequent confusion arises among
-ecologists over the use of these two terms, especially in a
-probabilistic context. Indeed, in many studies of probabilistic
-ecological networks, it remains unclear when authors describe potential
-or realized interactions, or when so-called probabilities are actually
-\emph{interaction scores}. A better understanding of these differences
-would alleviate interpretation errors and help ecologists use these
-numbers more appropriately.
+The first aspect to take into consideration when estimating or
+interpreting probabilities of interactions is knowing if they describe
+the likelihood of potential or realized interactions. A potential
+interaction is defined as the biological capacity of two species to
+interact (i.e., the probability that they \emph{can} interact) whereas a
+realized interaction refers to the materialization or observation of
+this interaction in a delineated space and time period (i.e., the
+probability that they interact). Here, we will use the terms
+\emph{metaweb} to designate networks of potential interactions and
+\emph{local networks} for those of realized interactions. Frequent
+confusion arises among ecologists over the use of these two terms,
+especially in a probabilistic context. Indeed, in many studies of
+probabilistic ecological networks, it remains unclear when authors
+describe potential or realized interactions, or when so-called
+probabilities are actually \emph{interaction scores}. Likewise,
+probabilistic potential interactions are often used as realized
+interactions (and conversely), even when the type of interaction is
+clearly indicated. We believe that a better understanding of these
+differences and concepts would alleviate interpretation errors and help
+ecologists use these numbers more appropriately.
 
@@
 We can express the probability that two taxa \(i\) and \(j\) can
-interact as
+interact in a metaweb \(M\) as
 
-\begin{equation}\protect\hypertarget{eq:metaweb}{}{P(i \rightarrow j),}\label{eq:metaweb}\end{equation}
+\begin{equation}\protect\hypertarget{eq:metaweb}{}{P_{M}(i \rightarrow j),}\label{eq:metaweb}\end{equation}
 
@@
 interaction of \(1\); we know that they \emph{can} interact. This means
-that rare interactions can be given high probabilities in the metaweb.
-Unobserved interactions, on the other hand, are given lower
+that rare interactions can technically be given high probabilities in
+the metaweb. Unobserved interactions, on the other hand, are given lower
 probabilities, going as low as \(0\) for forbidden links. Two important
@@
 
-One potential application of metawebs is the prediction of networks of
-realized interactions. Even though the spatiotemporal variation of
-interactions is not considered in metawebs, they can nevertheless be a
-useful tool to reconstruct local networks. First, metawebs set the upper
-limit of species interactions, i.e.~the probability that two species
-interact at a specific location is always lower than the probability of
-their potential interaction
-(\(P(i \rightarrow j) < P(i \rightarrow j | x_1, x_2, ...)\)). This
-implies that predicting local networks from metawebs realistically might
-need be done by filtering out interactions from its subnetworks. Second,
-the structure of local networks is constrained by the one of their
-metaweb. Inferring their structure from the metaweb first could help
-predicting which potential interactions are not realized. Ultimately, we
-believe that predicting probabilistic local networks from metawebs must
-be done with caution, as long as uncertainty is adequately propagated.
-
 \hypertarget{probabilistic-local-networks}{%
@@
 
-\[P(i \rightarrow j | C, A, N, E, t)\]
+As opposed to metawebs, probabilistic local food webs represent the
+likelihood that two species will interact at a specific location and
+within a given time period; in other words, they are context dependant.
+To be specific, space is defined here as the geographic coordinates (\$
+\bold x,
+\bold y\() of the spatial boundaries delineating the system, whereas time is the time interval (\)
+\bold t\$) during which interactions were sampled or for which they were
+predicted. We put these variables in bold to emphasize that they are not
+single values, but rather continued dimensions that could be outlined
+differently depending on the study system. Regardless of how they were
+defined, they always delineate a specific area \(A\) and duration \(D\).
+These could refer to the sampled area and duration or to the targeted
+location and time period.
 
-i = predator j = prey C = co-occurrence (and relative abundance?) A =
-area N = relative abundance (or network?) E = environment (including
-network?) t = time
+Many factors could be taken into consideration when estimating the
+probability that a predator species \(i\) interacts with a given prey
+species \(j\) locally. One of the most important is species
+co-occurrence, which describes if both species can be found at location
+and time (\$ \bold x, \bold y, \bold t\$). Surely, the probability that
+the interaction is realized must be \(0\) when species do not co-occur.
+Similarly, species relative abundance is another important predictor of
+the probability of interaction, because it impacts the probability that
+species will randomly encounter (Canard \emph{et al.} 2012; Canard
+\emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
+probabilities can also be conditional on other biological and
+environmental variables, such as temperature, precipitation, presence of
+shelters, phenotypic plasticity, phenology, and presence of other
+interacting species in the network. These conditions can affect species
+traits, which greatly impact the likelihood of interactions (Poisot
+\emph{et al.} 2015). When probabilities of interactions are estimated
+using specific values of these variables, ecologists should make them
+explicit in their metadata, preferably using mathematical equations to
+avoid any ambiguity. In the next section, we will see examples of why
+this matters when it comes to spatial, temporal, and taxonomic scaling
+of biotic interactions. Here, we will use the variable \(\bold \Omega\)
+as a substitute for the biological and ecological context in which
+interaction probabilities were estimated. This gives us the following
+equation for the probability that species (or taxa) \(i\) and \(j\)
+interact in a local network \(N\):
 
-What does a probability in the context of a local network mean? A
-cautionary tale of how we define probabilities.
+\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega).}\label{eq:local}\end{equation}
+
+\hypertarget{from-potential-to-realized-interactions}{%
+\subsection{From potential to realized
+interactions}\label{from-potential-to-realized-interactions}}
+
+Even though the spatiotemporal variation of interactions is not
+considered in metawebs, they can still be useful to reconstruct local
+networks of realized interactions. Indeed, local networks are formed
+from subsets of their metaweb (called subnetworks), which are obtained
+by selecting a subset of both species and interactions (Dunne 2006).
+Because a community's composition is arguably easier to sample (or
+predict) than its interactions, the biggest challenge is to sample links
+from the metaweb. This becomes a conceptual issue when we consider how
+potential and realized interactions differ. Despite these concerns,
+metawebs remain an important source of ecological information that can
+be leveraged for realistically predicting spatially explicit networks.
+First, metawebs set the upper limit of species interactions (McLeod
+\emph{et al.} 2021), i.e. the probability that two species interact at a
+specific location is always lower or equal to the probability of their
+potential interaction:
+
+\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega) \le P_M(i
+\rightarrow j).}\label{eq:switch}\end{equation}
+
+Therefore, building local networks from their metaweb keeping the same
+values of interaction probability would generate systematic biases in
+the prediction. Second, the structure of local networks is constrained
+by the one of their metaweb (Saravia \emph{et al.} 2022). This suggests
+that a metaweb not only constraints the pairwise interactions of its
+corresponding local networks, but also their emerging properties.
+Inferring the structure of local networks from the metaweb could thus
+help estimate more realistically the likelihood that potential
+interactions are realized and observed locally (Strydom \emph{et al.}
+2021).
+
+\hypertarget{scaling}{%
+\section{Scaling}\label{scaling}}
 
@@
 \tightlist
-\item
-  It means the probability that two taxa will interact at a given
-  location.
-\item
-  What do we mean by saying that two taxa will interact? We usually mean
-  that at least one individual from one group will interact with (e.g.,
-  predate) at least one other individual from the other group.
-\item
-  The probability is conditional on the environmental and local
-  abundance contexts.
 \item
@@
 \end{itemize}
-
-\hypertarget{scaling}{%
-\section{Scaling}\label{scaling}}
 
@@
 
+\leavevmode\hypertarget{ref-Canard2014EmpEva}{}%
+Canard, E.F., Mouquet, N., Mouillot, D., Stanko, M., Miklisova, D. \&
+Gravel, D. (2014). Empirical Evaluation of Neutral Interactions in
+Host-Parasite Networks. \emph{The American Naturalist}, 183, 468--479.
+
+\leavevmode\hypertarget{ref-Canard2012EmeStr}{}%
+Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
+Mouillot, D. (2012). Emergence of Structural Patterns in Neutral Trophic
+Networks. \emph{PLOS ONE}, 7, e38295.
+
 \leavevmode\hypertarget{ref-Catchen2023Missinga}{}%
@@
 
+\leavevmode\hypertarget{ref-Saravia2022EcoNet}{}%
+Saravia, L.A., Marina, T.I., Kristensen, N.P., De Troch, M. \& Momo,
+F.R. (2022). Ecological network assembly: How the regional metaweb
+influences local food webs. \emph{Journal of Animal Ecology}, 91,
+630--642.
+
 \leavevmode\hypertarget{ref-Strydom2022Food}{}%

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@3c781c57e4f4e2b868da5537661c119495370a97 🚀

@@
 within a given time period; in other words, they are context dependant.
-To be specific, space is defined here as the geographic coordinates (\$
-\bold x,
-\bold y\() of the spatial boundaries delineating the system, whereas time is the time interval (\)
-\bold t\$) during which interactions were sampled or for which they were
-predicted. We put these variables in bold to emphasize that they are not
-single values, but rather continued dimensions that could be outlined
-differently depending on the study system. Regardless of how they were
-defined, they always delineate a specific area \(A\) and duration \(D\).
-These could refer to the sampled area and duration or to the targeted
-location and time period.
+To be specific, space is defined here as the geographic coordinates \$
+\bold x, \bold y\$ of the spatial boundaries delineating the system,
+whereas time is the time interval (\$ \bold t\$) during which
+interactions were sampled or for which they were predicted. We put these
+variables in bold to emphasize that they are not single values, but
+rather continued dimensions that could be outlined differently depending
+on the study system. Regardless of how they were defined, they always
+delineate a specific area \(A\) and duration \(D\). These could refer to
+the sampled area and duration or to the targeted location and time
+period.
 
@@
 co-occurrence, which describes if both species can be found at location
-and time (\$ \bold x, \bold y, \bold t\$). Surely, the probability that
+and time \$ \bold x, \bold y, \bold t\$. Surely, the probability that
 the interaction is realized must be \(0\) when species do not co-occur.

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@eb3049b5587cebcac0a700128f22895c74428da6 🚀

@@
 \bold x, \bold y\$ of the spatial boundaries delineating the system,
-whereas time is the time interval (\$ \bold t\$) during which
-interactions were sampled or for which they were predicted. We put these
-variables in bold to emphasize that they are not single values, but
-rather continued dimensions that could be outlined differently depending
-on the study system. Regardless of how they were defined, they always
-delineate a specific area \(A\) and duration \(D\). These could refer to
-the sampled area and duration or to the targeted location and time
-period.
+whereas time is the time interval \$ \bold t\$ during which interactions
+were sampled or for which they were predicted. We put these variables in
+bold to emphasize that they are not single values, but rather continued
+dimensions that could be outlined differently depending on the study
+system. Regardless of how they were defined, they always delineate a
+specific area \(A\) and duration \(D\). These could refer to the sampled
+area and duration or to the targeted location and time period.
 

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@0e0d41cde16c07b04c9d5e5f4f0fa52d636046ad 🚀

@@
 To be specific, space is defined here as the geographic coordinates \$
-\bold x, \bold y\$ of the spatial boundaries delineating the system,
-whereas time is the time interval \$ \bold t\$ during which interactions
-were sampled or for which they were predicted. We put these variables in
-bold to emphasize that they are not single values, but rather continued
-dimensions that could be outlined differently depending on the study
-system. Regardless of how they were defined, they always delineate a
-specific area \(A\) and duration \(D\). These could refer to the sampled
-area and duration or to the targeted location and time period.
+\mathbf x, \mathbf y\$ of the spatial boundaries delineating the system,
+whereas time is the time interval \$ \mathbf t\$ during which
+interactions were sampled or for which they were predicted. We put these
+variables in bold to emphasize that they are not single values, but
+rather continued dimensions that could be outlined differently depending
+on the study system. Regardless of how they were defined, they always
+delineate a specific area \(A\) and duration \(D\). These could refer to
+the sampled area and duration or to the targeted location and time
+period.
 
@@
 co-occurrence, which describes if both species can be found at location
-and time \$ \bold x, \bold y, \bold t\$. Surely, the probability that
-the interaction is realized must be \(0\) when species do not co-occur.
-Similarly, species relative abundance is another important predictor of
-the probability of interaction, because it impacts the probability that
-species will randomly encounter (Canard \emph{et al.} 2012; Canard
-\emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
+and time \$ \mathbf x, \mathbf y, \mathbf t\$. Surely, the probability
+that the interaction is realized must be \(0\) when species do not
+co-occur. Similarly, species relative abundance is another important
+predictor of the probability of interaction, because it impacts the
+probability that species will randomly encounter (Canard \emph{et al.}
+2012; Canard \emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
 probabilities can also be conditional on other biological and
@@
 
-\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega).}\label{eq:local}\end{equation}
+\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega).}\label{eq:local}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega) \le P_M(i
+\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega) \le P_M(i
 \rightarrow j).}\label{eq:switch}\end{equation}

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@126a65373848fd673cccf86b0766cd1d8bf98a39 🚀

@@
 To be specific, space is defined here as the geographic coordinates \$
-\mathbf x, \mathbf y\$ of the spatial boundaries delineating the system,
-whereas time is the time interval \$ \mathbf t\$ during which
+\mathbf{x}, \mathbf{y}\$ of the spatial boundaries delineating the
+system, whereas time is the time interval \$ \mathbf{t}\$ during which
 interactions were sampled or for which they were predicted. We put these
@@
 co-occurrence, which describes if both species can be found at location
-and time \$ \mathbf x, \mathbf y, \mathbf t\$. Surely, the probability
-that the interaction is realized must be \(0\) when species do not
-co-occur. Similarly, species relative abundance is another important
-predictor of the probability of interaction, because it impacts the
-probability that species will randomly encounter (Canard \emph{et al.}
-2012; Canard \emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
-probabilities can also be conditional on other biological and
-environmental variables, such as temperature, precipitation, presence of
-shelters, phenotypic plasticity, phenology, and presence of other
-interacting species in the network. These conditions can affect species
-traits, which greatly impact the likelihood of interactions (Poisot
-\emph{et al.} 2015). When probabilities of interactions are estimated
-using specific values of these variables, ecologists should make them
-explicit in their metadata, preferably using mathematical equations to
-avoid any ambiguity. In the next section, we will see examples of why
-this matters when it comes to spatial, temporal, and taxonomic scaling
-of biotic interactions. Here, we will use the variable \(\bold \Omega\)
-as a substitute for the biological and ecological context in which
-interaction probabilities were estimated. This gives us the following
-equation for the probability that species (or taxa) \(i\) and \(j\)
-interact in a local network \(N\):
+and time \$ \mathbf{x}, \mathbf{y}, \mathbf{t}\$. Surely, the
+probability that the interaction is realized must be \(0\) when species
+do not co-occur. Similarly, species relative abundance is another
+important predictor of the probability of interaction, because it
+impacts the probability that species will randomly encounter (Canard
+\emph{et al.} 2012; Canard \emph{et al.} 2014; Poisot \emph{et al.}
+2015). Interaction probabilities can also be conditional on other
+biological and environmental variables, such as temperature,
+precipitation, presence of shelters, phenotypic plasticity, phenology,
+and presence of other interacting species in the network. These
+conditions can affect species traits, which greatly impact the
+likelihood of interactions (Poisot \emph{et al.} 2015). When
+probabilities of interactions are estimated using specific values of
+these variables, ecologists should make them explicit in their metadata,
+preferably using mathematical equations to avoid any ambiguity. In the
+next section, we will see examples of why this matters when it comes to
+spatial, temporal, and taxonomic scaling of biotic interactions. Here,
+we will use the variable \(\bold \Omega\) as a substitute for the
+biological and ecological context in which interaction probabilities
+were estimated. This gives us the following equation for the probability
+that species (or taxa) \(i\) and \(j\) interact in a local network
+\(N\):
 
@@
 
-\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega) \le P_M(i
+\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \mathbf x, \mathbf y, \mathbf t, \mathbf \Omega) \le
+P_M(i
 \rightarrow j).}\label{eq:switch}\end{equation}

### 2023-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@370422cc320937a7967023fc28ae6ca2199a04c4 🚀

--- 2023-02-10 draft.tex
@@
 within a given time period; in other words, they are context dependant.
-To be specific, space is defined here as the geographic coordinates \$
-\bold x, \bold y\$ of the spatial boundaries delineating the system,
-whereas time is the time interval \$ \bold t\$ during which interactions
-were sampled or for which they were predicted. We put these variables in
-bold to emphasize that they are not single values, but rather continued
-dimensions that could be outlined differently depending on the study
-system. Regardless of how they were defined, they always delineate a
-specific area \(A\) and duration \(D\). These could refer to the sampled
-area and duration or to the targeted location and time period.
+To be specific, space is defined here as the geographic coordinates
+\(x\), \(y\) of the spatial boundaries delineating the system, whereas
+time is the time interval \(t\) during which interactions were sampled
+or for which they were predicted. We want to point out that they are not
+single values, but rather continued dimensions that could be outlined
+differently depending on the study system. Regardless of how they were
+defined, they always delineate a specific area \(A\) and duration \(D\).
+These could refer to the sampled area and duration or to the targeted
+location and time period.
 
@@
 co-occurrence, which describes if both species can be found at location
-and time \$ \bold x, \bold y, \bold t\$. Surely, the probability that
-the interaction is realized must be \(0\) when species do not co-occur.
+and time \(x\), \(y\), \(t\). Surely, the probability that the
+interaction is realized must be \(0\) when species do not co-occur.
 Similarly, species relative abundance is another important predictor of
@@
 this matters when it comes to spatial, temporal, and taxonomic scaling
-of biotic interactions. Here, we will use the variable \(\bold \Omega\)
-as a substitute for the biological and ecological context in which
+of biotic interactions. Here, we will use the variable \(\Omega\) as a
+substitute for the biological and ecological context in which
 interaction probabilities were estimated. This gives us the following
@@
 
-\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega).}\label{eq:local}\end{equation}
+\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | x, y, t, \Omega).}\label{eq:local}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | \bold x, \bold y, \bold t, \bold \Omega) \le P_M(i
-\rightarrow j).}\label{eq:switch}\end{equation}
+\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | x, y, t, \Omega) \le
+P_M(i \rightarrow j).}\label{eq:switch}\end{equation}
 

### 2023-02-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@6f55f70290a06f30abd441eb8a2cae1bc8399fe1 🚀

@@
 uncertainties when building these types of networks. Therefore,
-important methodological and conceptual decisions must been made when
+important methodological and conceptual decisions must be made when
 sampling and building food webs.
@@
 nuances must however be made here. Because of observation errors due to
-taxonomic misidentifications and ecological misinterpretations, many
-observations of interactions are actually false positives. Similarly,
-forbidden interactions can be false negatives if e.g.~they have been
-assessed for specific phenotypes, locations or time. Implementing a
-Bayesian framework, which updates prior probabilities of interactions
-with empirical data, could lessen these errors.
+taxonomic misidentifications and ecological misinterpretations (e.g.,
+due to cryptic species and interactions; Pringle \& Hutchinson 2020),
+many observations of interactions are actually false positives.
+Similarly, forbidden interactions can be false negatives if e.g.~they
+have been assessed for specific phenotypes, locations or time.
+Implementing a Bayesian framework, which updates prior probabilities of
+interactions with empirical data, could lessen these errors.
 
@@
 To be specific, space is defined here as the geographic coordinates
-\(x\), \(y\) of the spatial boundaries delineating the system, whereas
+\((x, y)\) of the spatial boundaries delineating the system, whereas
 time is the time interval \(t\) during which interactions were sampled
@@
 differently depending on the study system. Regardless of how they were
-defined, they always delineate a specific area \(A\) and duration \(D\).
+defined, they always delineate a specific area \(A\) and duration \(t\).
 These could refer to the sampled area and duration or to the targeted
@@
 species \(j\) locally. One of the most important is species
-co-occurrence, which describes if both species can be found at location
-and time \(x\), \(y\), \(t\). Surely, the probability that the
-interaction is realized must be \(0\) when species do not co-occur.
-Similarly, species relative abundance is another important predictor of
-the probability of interaction, because it impacts the probability that
+co-occurrence \(C\), which is a Boolean describing if both species can
+be found at location and time (\(x\), \(y\), \(t\)). Surely, the
+probability that the interaction is realized must be \(0\) when species
+do not co-occur (\(C = 0\)). Interaction probabilities can also be
+conditional on other biological and environmental variables, such as
+temperature, precipitation, presence of shelters, phenotypic plasticity,
+phenology, and presence of other interacting species in the network.
+These conditions can affect species traits, which greatly impact the
+capacity of species to interact (Poisot \emph{et al.} 2015). Similarly,
+species relative abundance is another important predictor of the
+probability of interaction, because it impacts the probability that
 species will randomly encounter (Canard \emph{et al.} 2012; Canard
-\emph{et al.} 2014; Poisot \emph{et al.} 2015). Interaction
-probabilities can also be conditional on other biological and
-environmental variables, such as temperature, precipitation, presence of
-shelters, phenotypic plasticity, phenology, and presence of other
-interacting species in the network. These conditions can affect species
-traits, which greatly impact the likelihood of interactions (Poisot
-\emph{et al.} 2015). When probabilities of interactions are estimated
-using specific values of these variables, ecologists should make them
-explicit in their metadata, preferably using mathematical equations to
-avoid any ambiguity. In the next section, we will see examples of why
-this matters when it comes to spatial, temporal, and taxonomic scaling
-of biotic interactions. Here, we will use the variable \(\Omega\) as a
-substitute for the biological and ecological context in which
-interaction probabilities were estimated. This gives us the following
-equation for the probability that species (or taxa) \(i\) and \(j\)
-interact in a local network \(N\):
+\emph{et al.} 2014; Poisot \emph{et al.} 2015). Here, we will use the
+variable \(\Omega\) as a substitute for the biological and ecological
+context in which interaction probabilities were estimated. This gives us
+the following equation for the probability of realized interaction
+between species (or taxa) \(i\) and \(j\) in a local network \(N\):
 
-\begin{equation}\protect\hypertarget{eq:local}{}{P_N(i \rightarrow j | x, y, t, \Omega).}\label{eq:local}\end{equation}
+\begin{equation}\protect\hypertarget{eq:local}{}{P_{N}(i \rightarrow j | A, t, C, \Omega),}\label{eq:local}\end{equation}
+
+which can be read as the probability of local interaction between the
+two species in an area \(A\) and time interval \(t\), given their
+co-occurrence \(C\) and specific environmental and biological conditions
+\(\Omega\).
+
+Multiple difficulties of interpretation arise when the conditions are
+not clearly specified, which we found is often the case in the
+literature. For example, if \(P_{N}(i \rightarrow j | C = 1)\)
+represents the probability that two co-occurring species interact (i.e.,
+the edge's probability value), \(P_{N}(i \rightarrow j)\) denotes
+instead the probability of interaction without knowing if they co-occur
+(i.e., the product of the nodes and edge's probability values). For
+practical reasons, probabilistic ecological networks are generally
+represented as matrices of probabilities (i.e., matrices of edges
+without node values), whose elements are thus hard to interpret without
+clear indications about \(C\). Overall, when probabilities of
+interactions are estimated using specific values of \(A\), \(t\), \(C\),
+and \(\Omega\), ecologists should make them explicit in their metadata,
+preferably using mathematical equations to avoid any ambiguity. Below,
+we will see examples of why this matters when it comes to spatial,
+temporal, and taxonomic scaling of biotic interactions.
 
@@
 
-Even though the spatiotemporal variation of interactions is not
+Even though the spatiotemporal variability of interactions is not
 considered in metawebs, they can still be useful to reconstruct local
@@
 
-\begin{equation}\protect\hypertarget{eq:switch}{}{P_N(i \rightarrow j | x, y, t, \Omega) \le
+\begin{equation}\protect\hypertarget{eq:switch}{}{P_{N}(i \rightarrow j | A, t, C, \Omega) \le
 P_M(i \rightarrow j).}\label{eq:switch}\end{equation}
 
-Therefore, building local networks from their metaweb keeping the same
+Therefore, inferring local networks from their metaweb keeping the same
 values of interaction probability would generate systematic biases in
-the prediction. Second, the structure of local networks is constrained
-by the one of their metaweb (Saravia \emph{et al.} 2022). This suggests
-that a metaweb not only constraints the pairwise interactions of its
-corresponding local networks, but also their emerging properties.
-Inferring the structure of local networks from the metaweb could thus
-help estimate more realistically the likelihood that potential
-interactions are realized and observed locally (Strydom \emph{et al.}
-2021).
+the prediction. In that case, these networks would instead be called
+\emph{spatially explicit} or \emph{local} metawebs (i.e., smaller-scale
+networks of potential interactions). Second, the structure of local
+networks is constrained by the one of their metaweb (Saravia \emph{et
+al.} 2022). This suggests that a metaweb not only constrains the
+pairwise interactions of its corresponding local networks, but also
+their emerging properties. Inferring the structure of local networks
+from the metaweb could thus help estimate more realistically the
+likelihood that potential interactions are realized and observed locally
+(Strydom \emph{et al.} 2021).
 
@@
   regional networks inform local networks?
+\item
+  Sampling local networks from metawebs vs from probabilistic local
+  networks
 \end{itemize}
@@
 
-\hypertarget{concluding-remarks}{%
-\section{Concluding remarks}\label{concluding-remarks}}
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
-Here we present some advice moving forward.
+The emergence of probabilistic thinking in network ecology has paved the
+way to a better assessment of the spatiotemporal variability and
+uncertainty of biotic interactions. However, we showed that network
+metadata are perhaps as important as interaction data themselves when it
+comes to interpreting probabilistic food webs in ecological terms.
+First, the type of probabilistic interaction (potential or realized)
+impacts the importance of scale, with interactions in metawebs being
+scale independent, both spatially and temporally. Second, the conditions
+in which local networks were estimated (e.g., area, time, biological and
+environmental factors) and the attributes of the interacting species
+that were considered (e.g., species co-occurrence) are essential
+contextual factors that impact the mathematical representation of
+probabilities and their resulting behaviour. Third, the biological
+interpretation of probabilities changes with the level of organization
+of the network due to the aggregation of individuals into broader
+groups. All these information should be available as clear metadata so
+that ecologists can use probabilistic network data appropriately.
 
-\begin{itemize}
-\tightlist
-\item
-  What can we learn from other systems/fields (e.g., social networks,
-  probabilistic graph theory)?
-\item
-  What even are probabilities? What is the probability that we will ever
-  know the answer to that?
-\item
-  Be careful of how we define probabilities. Be sure to be explicit
-  about these things. Be sure to specify the type of interaction, the
-  spatial, temporal, and taxonomic scale when presenting new data on
-  interaction probabilities. We need better metadata documentation.
-\item
-  Be careful to use and manipulate interaction probabilities properly
-  depending on how they were defined and obtained. Different
-  interpretations imply different scaling, and thus different ways to
-  manipulate these numbers.
-\item
-  Maybe mention thinking about a workflow to predict probabilistic local
-  food webs from probabilistic metawebs.
-\end{itemize}
+Moreover, many statistical models in ecology that yield accurate
+predictions of biotic interactions are black boxes difficult to
+interpret. Ecologists should be careful before using the output of these
+models as probabilistic objects, since there is often a thin line
+between a real probability and a non-probabilistic predictive number (or
+score). Probabilities are numbers between \(0\) and \(1\) that sum to
+\(1\) and either represent the expected frequency of a phenomenon or the
+degree of belief that it will be realized. Non-probabilistic scores,
+which are more akin to interaction weights, have different mathematical
+properties, which impacts how we should handle these numbers in a
+spatially or temporally explicit context. Therefore, researchers should
+use their expertise to assess if their interaction data are actually
+probabilities or scores. This should also be added to the metadata
+before sharing them, as well as the methods used to build the networks.
+
+Better metadata documentation would allow researchers to use and
+manipulate probabilistic ecological interactions according to how they
+were actually defined and obtained. This would support better scientific
+practices, in particular when these data are used for ecological
+prediction and forecasting. For instance, we showed that building a
+rigorous workflow to predict local networks from a probabilistic metaweb
+requires a good understanding of the data at hand. Similarly, explicitly
+stating the context in which probabilistic data were estimated would
+help using forecasting food-web models more rigorously under specific
+climate change and habitat use scenarios. Regardless of the method and
+application, fostering a better foundation for probabilistic reasonings
+in network ecology, from the very nature of probabilities and biotic
+interactions, is essential.
 
@@
 
+\leavevmode\hypertarget{ref-Pringle2020ResFoo}{}%
+Pringle, R.M. \& Hutchinson, M.C. (2020). Resolving Food-Web Structure.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, 51, 55--80.
+
 \leavevmode\hypertarget{ref-Proulx2005NetThi}{}%

### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@7b0a67c1cad22368cc1a4c1cd050a0bae96a158a 🚀

@@
 availability of other prey species) factors contribute to this
-variability by impacting species co-occurrence (Araujo \emph{et al.}
-2011) and the realization of their interactions (Poisot \emph{et al.}
-2015). In this context, the development of computational methods in
-ecology can help alleviate the colossal sampling efforts required to
-document species interactions across time and space (Strydom \emph{et
-al.} 2021). Having a better portrait of species interactions and the
-emerging structure of their food webs is important since it lays the
-groundwork for understanding the functioning, dynamics, and resilience
-of ecosystems worldwide (e.g., Proulx \emph{et al.} 2005; Pascual
-\emph{et al.} 2006; Delmas \emph{et al.} 2019).
+variability by impacting species co-occurrence
+(\textbf{Araujo2011UsiSpe?}) and the realization of their interactions
+(Poisot \emph{et al.} 2015). In this context, the development of
+computational methods in ecology can help alleviate the colossal
+sampling efforts required to document species interactions across time
+and space (Strydom \emph{et al.} 2021). Having a better portrait of
+species interactions and the emerging structure of their food webs is
+important since it lays the groundwork for understanding the
+functioning, dynamics, and resilience of ecosystems worldwide (e.g.,
+\textbf{Proulx2005NetThi?}; \textbf{Pascual2006EcoNet?};
+\textbf{Delmas2019AnaEco?}).
 
@@
 have been developed to describe the structure (Poisot \emph{et al.}
-2016) and diversity (Ohlmann \emph{et al.} 2019; Godsoe \emph{et al.}
-2022) of probabilistic interactions, which shows the potential of this
-framework in the study of a variety of ecological phenomena.
+2016) and diversity (\textbf{Ohlmann2019DivInd?};
+\textbf{Godsoe2022SpeInt?}) of probabilistic interactions, which shows
+the potential of this framework in the study of a variety of ecological
+phenomena.
 
@@
 The basic unit of food webs and other ecological networks are
-individuals that interact with each others (e.g., by predation; Elton
-2001), forming individual-based networks. The aggregation of these
-individuals into more or less homogeneous groups (e.g., populations,
-species, trophic species, families) allows us to represent networks at
-broader scales, which impacts the properties and behaviour of these
-systems (Guimarães 2020). A network's nodes can thus designate distinct
-levels of organization, whereas the edges linking these nodes can
-describe a variety of interaction measures. When using a Boolean
-(yes-no) representation of biotic interactions, the observation that one
-individual from group (or node) \(i\) interacts with another individual
-from group \(j\) is enough to set the interaction \(A_{i,j}\) to 1. This
-simplified representation of food webs is a highly valuable source of
-ecological information (Pascual \emph{et al.} 2006) even though it
-overlooks important factors regarding interaction strengths. These, in
-turn, can be represented using weighted interactions, which better
-describe the energy flows, demographic impacts or frequencies of
-interactions between nodes (Berlow \emph{et al.} 2004; Borrett \&
-Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\)
-depending on the measure. For example, they can be used to estimate the
-average number of prey individuals consumed by the predators in a given
-time period. This extra amount of ecological information typically comes
-at a cost of greater sampling effort or data requirement in predictive
-models (Strydom \emph{et al.} 2021), which can lead to high
-uncertainties when building these types of networks. Therefore,
-important methodological and conceptual decisions must be made when
-sampling and building food webs.
+individuals that interact with each others (e.g., by predation;
+\textbf{Elton2001AniEco?}), forming individual-based networks. The
+aggregation of these individuals into more or less homogeneous groups
+(e.g., populations, species, trophic species, families) allows us to
+represent networks at broader scales, which impacts the properties and
+behaviour of these systems (\textbf{Guimaraes2020StrEco?}). A network's
+nodes can thus designate distinct levels of organization, whereas the
+edges linking these nodes can describe a variety of interaction
+measures. When using a Boolean (yes-no) representation of biotic
+interactions, the observation that one individual from group (or node)
+\(i\) interacts with another individual from group \(j\) is enough to
+set the interaction \(A_{i,j}\) to 1. This simplified representation of
+food webs is a highly valuable source of ecological information
+(\textbf{Pascual2006EcoNet?}) even though it overlooks important factors
+regarding interaction strengths. These, in turn, can be represented
+using weighted interactions, which better describe the energy flows,
+demographic impacts or frequencies of interactions between nodes
+(\textbf{Berlow2004IntStr?}; \textbf{Borrett2019WalPar?}), with
+\(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\) depending on the measure.
+For example, they can be used to estimate the average number of prey
+individuals consumed by the predators in a given time period. This extra
+amount of ecological information typically comes at a cost of greater
+sampling effort or data requirement in predictive models (Strydom
+\emph{et al.} 2021), which can lead to high uncertainties when building
+these types of networks. Therefore, important methodological and
+conceptual decisions must be made when sampling and building food webs.
 
@@
 taxonomic misidentifications and ecological misinterpretations (e.g.,
-due to cryptic species and interactions; Pringle \& Hutchinson 2020),
+due to cryptic species and interactions; \textbf{Pringle2020ResFoo?}),
 many observations of interactions are actually false positives.
@@
 probability of interaction, because it impacts the probability that
-species will randomly encounter (Canard \emph{et al.} 2012; Canard
-\emph{et al.} 2014; Poisot \emph{et al.} 2015). Here, we will use the
-variable \(\Omega\) as a substitute for the biological and ecological
-context in which interaction probabilities were estimated. This gives us
-the following equation for the probability of realized interaction
-between species (or taxa) \(i\) and \(j\) in a local network \(N\):
+species will randomly encounter (Poisot \emph{et al.} 2015;
+\textbf{Canard2012EmeStr?}; \textbf{Canard2014EmpEva?}). Here, we will
+use the variable \(\Omega\) as a substitute for the biological and
+ecological context in which interaction probabilities were estimated.
+This gives us the following equation for the probability of realized
+interaction between species (or taxa) \(i\) and \(j\) in a local network
+\(N\):
 
@@
 temporal, and taxonomic scaling of biotic interactions.
+
+{[}Table 1 about here{]}. Articles using probabilistic interactions and
+the definitions and variables they considered.
 
@@
 networks of potential interactions). Second, the structure of local
-networks is constrained by the one of their metaweb (Saravia \emph{et
-al.} 2022). This suggests that a metaweb not only constrains the
-pairwise interactions of its corresponding local networks, but also
-their emerging properties. Inferring the structure of local networks
-from the metaweb could thus help estimate more realistically the
-likelihood that potential interactions are realized and observed locally
-(Strydom \emph{et al.} 2021).
+networks is constrained by the one of their metaweb
+(\textbf{Saravia2022EcoNet?}). This suggests that a metaweb not only
+constrains the pairwise interactions of its corresponding local
+networks, but also their emerging properties. Inferring the structure of
+local networks from the metaweb could thus help estimate more
+realistically the likelihood that potential interactions are realized
+and observed locally (Strydom \emph{et al.} 2021).
+
+{[}Figure 1 about here{]}. Empirical example of the association between
+the number of interactions in realized local food webs and the number of
+interactions in the corresponding subnetworks of their regional metaweb.
+We should expect the association to be linear below the 1:1 line,
+illustrating eq.~\ref{eq:switch}.
 
@@
 \section{Scaling}\label{scaling}}
-
-\begin{itemize}
-\tightlist
-\item
-  We should expect a certain number of interactions to be realized
-  depending on the probability value. This number depends on the number
-  of trials, which also depends on the ecological context (e.g.,
-  environmental conditions, scale) in which probabilities were
-  estimated. This is in contrast with probabilities in metawebs.
-\end{itemize}
 
@@
 
-How do interaction probabilities scale spatially and temporally?
+Metawebs and local networks intrinsically differ in their relation to
+scale. On one hand, as mentioned above, probabilistic metawebs are
+context independent, i.e., probabilistic pairwise interactions do not
+scale with space and time because they depend solely on the biological
+capacity of the two taxa to interact. This implies that the estimated
+likelihood that two species can potentially interact should be the same
+among all metawebs in which they are present. In practice, this is
+rarely the case because ecologists use different methods and data to
+estimate these probabilities of interactions. However, in the case where
+local metawebs \(M_{x,y}\) are subsampled from their regional
+counterpart \(M_0\), we should expect edge values to be identical among
+all networks, regardless of their spatial scale,
+i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
+other hand, local probabilistic networks are indissociable from their
+spatial and temporal contexts because there are more opportunities of
+interactions (e.g., more individuals, more trait variations, more chance
+of encounter) in a larger area and longer time period (McLeod \emph{et
+al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
+an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
+\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
+to scale spatially, i.e.
+\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
+Similarly, the temporal scaling of probabilistic local food webs could
+be manifested through the effect of sampling effort on the observation
+of interactions (McLeod \emph{et al.} 2021;
+\textbf{Jordano2016Samplinga?}) or of time itself on their realization
+(Poisot \emph{et al.} 2012). There are many network-area relationships
+(e.g., Wood \emph{et al.} 2015; Galiana \emph{et al.} 2018) and
+interaction accumulation curves (e.g, \textbf{Jordano2016Samplinga?})
+explored in the literature. These could inspire the development and
+testing of different equations describing the spatiotemporal scaling of
+probabilistic pairwise interactions in local networks, which are over
+the scope of this manuscript.
+
+Another conceptual challenge encountered when using probabilistic food
+webs is the prediction of Boolean networks across space. Lets take
+\(n \times n\) grid cells each representing a probabilistic food web. If
+they contain potential interactions, a single random trial must be
+conducted for each pairwise interaction across the region (i.e., we
+should have only one random realization of the regional metaweb). On the
+contrary, if they represent probabilities of realized interactions, each
+food web must be independently sampled (i.e., \(n^2\) independent random
+draws). This has direct implications on the spatial scaling of
+interactions. For example, let \(N_2\) be another network of area
+\(A_2 < A_0\) within \(A_0\) and disjoint from \(N_1\), such as \$ N\_1
+\cup N\_2 = N\_0\$ (think of two contiguous cells that together
+delineate \(N_0\)). All other things being equal, we should expect the
+probability that \(i\) and \(j\) interacts in \(A_0\) to be
+\(P_{N_0}(i \rightarrow j) = 1 - (1 - P_{N_1}(i \rightarrow j)) \times (1 - P_{N_2}(i \rightarrow j))\)
+if \(N_1\) and \(N_2\) are independently sampled. This also implies that
+we should expect interactions to be realized in a certain number of
+local networks depending on the probability value, which is not the case
+with metawebs. Note that spatial auto-correlation and the concept of
+meta-network (i.e., networks of networks) could invalidate the
+statistical assumption of independence. Nevertheless, the fundamental
+difference in sampling metawebs and local networks stands even when
+considering these factors. This difference in sampling further sheds
+light on the importance of clearly defining interaction probabilities.
+What we consider as a \emph{Bernoulli trial}, when randomly drawing
+deterministic networks from probabilistic food webs, depends on our
+biological interpretation of these probabilities.
 
@@
 \item
-  Why do probabilistic local food webs scale with area and time but not
-  probabilistic metawebs?
-\item
-  In metawebs, interaction probabilities do not scale with space and
-  time because they depend solely on the biological capacity of two
-  species to interact.
-\item
-  In local food webs, interaction probabilities scale with space and
-  time because there are more opportunities of interactions (e.g., more
-  environmental conditions) in a larger area and longer time period.
-\item
-  What are some network area relationships in probabilistic local food
-  webs?
-\item
-  We know that local networks can inform regional networks. However, can
-  regional networks inform local networks?
-\item
-  Sampling local networks from metawebs vs from probabilistic local
-  networks
+  Making interaction probabilities spatiotemporally explicit
 \end{itemize}
 
-\textbf{Figure:} Empirical example of the association between the number
-of interactions in realized local food webs and the number of
-interactions in the corresponding species subnetworks of regional
-networks. We should expect the interaction to be linear below the 1:1
-line.
-
-\textbf{Papers:} there might be something in these McLeod \emph{et al.}
-(2020); McLeod \emph{et al.} (2021); Wood \emph{et al.} (2015)
+{[}Figure 2 about here{]}. Conceptual figure showing (1) the
+spatiotemporal scaling of probabilistic metawebs and local food webs and
+(2) the spatial sampling of metawebs and local food webs into Boolean
+networks.
 
@@
 
-\textbf{Figure:} Conceptual figure of how a scale up of the nodes from
-an individual to a population to any higher taxonomic group change our
-interpretation of the probability of interaction.
+{[}Figure 3 about here{]}. Conceptual figure of how a scale up of the
+nodes from an individual to a population to any higher taxonomic group
+change our interpretation of the probability of interaction.
 
@@
 
-\leavevmode\hypertarget{ref-Araujo2011UsiSpe}{}%
-Araujo, M.B., Rozenfeld, A., Rahbek, C. \& Marquet, P.A. (2011). Using
-species co-occurrence networks to assess the impacts of climate change.
-\emph{Ecography}, 34, 897--908.
-
-\leavevmode\hypertarget{ref-Berlow2004IntStr}{}%
-Berlow, E.L., Neutel, A.-M., Cohen, J.E., De Ruiter, P.C., Ebenman, B.,
-Emmerson, M., \emph{et al.} (2004). Interaction strengths in food webs:
-Issues and opportunities. \emph{Journal of Animal Ecology}, 73,
-585--598.
-
 \leavevmode\hypertarget{ref-Blanchet2020Cooccurrencea}{}%
@@
 1050--1063.
-
-\leavevmode\hypertarget{ref-Borrett2019WalPar}{}%
-Borrett, S.R. \& Scharler, U.M. (2019). Walk partitions of flow in
-Ecological Network Analysis: Review and synthesis of methods and
-indicators. \emph{Ecological Indicators}, 106, 105451.
-
-\leavevmode\hypertarget{ref-Canard2014EmpEva}{}%
-Canard, E.F., Mouquet, N., Mouillot, D., Stanko, M., Miklisova, D. \&
-Gravel, D. (2014). Empirical Evaluation of Neutral Interactions in
-Host-Parasite Networks. \emph{The American Naturalist}, 183, 468--479.
-
-\leavevmode\hypertarget{ref-Canard2012EmeStr}{}%
-Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
-Mouillot, D. (2012). Emergence of Structural Patterns in Neutral Trophic
-Networks. \emph{PLOS ONE}, 7, e38295.
 
@@
 
-\leavevmode\hypertarget{ref-Delmas2019AnaEco}{}%
-Delmas, E., Besson, M., Brice, M.-H., Burkle, L.A., Dalla Riva, G.V.,
-Fortin, M.-J., \emph{et al.} (2019). Analysing ecological networks of
-species interactions. \emph{Biological Reviews}, 94, 16--36.
-
 \leavevmode\hypertarget{ref-Dunne2006Network}{}%
@@
 
-\leavevmode\hypertarget{ref-Elton2001AniEco}{}%
-Elton, C.S. (2001). \emph{Animal Ecology}. University of Chicago Press,
-Chicago, IL.
-
-\leavevmode\hypertarget{ref-Godsoe2022SpeInt}{}%
-Godsoe, W., Murray, R. \& Iritani, R. (2022). Species interactions and
-diversity: A unified framework using Hill numbers. \emph{Oikos}, n/a,
-e09282.
+\leavevmode\hypertarget{ref-Galiana2018SpaSca}{}%
+Galiana, N., Lurgi, M., Claramunt-López, B., Fortin, M.-J., Leroux, S.,
+Cazelles, K., \emph{et al.} (2018). The spatial scaling of species
+interaction networks. \emph{Nature Ecology \& Evolution}, 2, 782--790.
 
@@
 700--710.
-
-\leavevmode\hypertarget{ref-Guimaraes2020StrEco}{}%
-Guimarães, P.R. (2020). The Structure of Ecological Networks Across
-Levels of Organization. \emph{Annual Review of Ecology, Evolution, and
-Systematics}, 51, 433--460.
 
@@
 
-\leavevmode\hypertarget{ref-Ohlmann2019DivInd}{}%
-Ohlmann, M., Miele, V., Dray, S., Chalmandrier, L., O'Connor, L. \&
-Thuiller, W. (2019). Diversity indices for ecological networks: A
-unifying framework using Hill numbers. \emph{Ecology Letters}, 22,
-737--747.
-
 \leavevmode\hypertarget{ref-Olesen2010Missing}{}%
@@
 Sciences}, 278, 725--732.
-
-\leavevmode\hypertarget{ref-Pascual2006EcoNet}{}%
-Pascual, M., Dunne, J.A. \& Dunne, J.A. (2006). \emph{Ecological
-Networks: Linking Structure to Dynamics in Food Webs}. Oxford University
-Press, USA.
 
@@
 
-\leavevmode\hypertarget{ref-Pringle2020ResFoo}{}%
-Pringle, R.M. \& Hutchinson, M.C. (2020). Resolving Food-Web Structure.
-\emph{Annual Review of Ecology, Evolution, and Systematics}, 51, 55--80.
-
-\leavevmode\hypertarget{ref-Proulx2005NetThi}{}%
-Proulx, S.R., Promislow, D.E.L. \& Phillips, P.C. (2005). Network
-thinking in ecology and evolution. \emph{Trends in Ecology \&
-Evolution}, SPECIAL issue: BUMPER book REVIEW, 20, 345--353.
-
 \leavevmode\hypertarget{ref-Pulliam1974Theory}{}%
@@
 Naturalist}, 108, 59--74.
-
-\leavevmode\hypertarget{ref-Saravia2022EcoNet}{}%
-Saravia, L.A., Marina, T.I., Kristensen, N.P., De Troch, M. \& Momo,
-F.R. (2022). Ecological network assembly: How the regional metaweb
-influences local food webs. \emph{Journal of Animal Ecology}, 91,
-630--642.
 

### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@352fcf20086a8dc1517ff49cafce3cb153734cd0 🚀

@@
 interactions. For example, let \(N_2\) be another network of area
-\(A_2 < A_0\) within \(A_0\) and disjoint from \(N_1\), such as \$ N\_1
-\cup N\_2 = N\_0\$ (think of two contiguous cells that together
+\(A_2 < A_0\) within \(A_0\) and disjoint from \(N_1\), such as \(N_1\)
+and \(N_2\) form \(N_0\) (think of two contiguous cells that together
 delineate \(N_0\)). All other things being equal, we should expect the

### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@be9661228c8024f390b240f4a8842821240fb010 🚀

@@
 availability of other prey species) factors contribute to this
-variability by impacting species co-occurrence
-(\textbf{Araujo2011UsiSpe?}) and the realization of their interactions
-(Poisot \emph{et al.} 2015). In this context, the development of
-computational methods in ecology can help alleviate the colossal
-sampling efforts required to document species interactions across time
-and space (Strydom \emph{et al.} 2021). Having a better portrait of
-species interactions and the emerging structure of their food webs is
-important since it lays the groundwork for understanding the
-functioning, dynamics, and resilience of ecosystems worldwide (e.g.,
-\textbf{Proulx2005NetThi?}; \textbf{Pascual2006EcoNet?};
-\textbf{Delmas2019AnaEco?}).
+variability by impacting species co-occurrence (Araujo \emph{et al.}
+2011) and the realization of their interactions (Poisot \emph{et al.}
+2015). In this context, the development of computational methods in
+ecology can help alleviate the colossal sampling efforts required to
+document species interactions across time and space (Strydom \emph{et
+al.} 2021). Having a better portrait of species interactions and the
+emerging structure of their food webs is important since it lays the
+groundwork for understanding the functioning, dynamics, and resilience
+of ecosystems worldwide (e.g., Proulx \emph{et al.} 2005; Pascual
+\emph{et al.} 2006; Delmas \emph{et al.} 2019).
 
@@
 have been developed to describe the structure (Poisot \emph{et al.}
-2016) and diversity (\textbf{Ohlmann2019DivInd?};
-\textbf{Godsoe2022SpeInt?}) of probabilistic interactions, which shows
-the potential of this framework in the study of a variety of ecological
-phenomena.
+2016) and diversity (Ohlmann \emph{et al.} 2019; Godsoe \emph{et al.}
+2022) of probabilistic interactions, which shows the potential of this
+framework in the study of a variety of ecological phenomena.
 
@@
 The basic unit of food webs and other ecological networks are
-individuals that interact with each others (e.g., by predation;
-\textbf{Elton2001AniEco?}), forming individual-based networks. The
-aggregation of these individuals into more or less homogeneous groups
-(e.g., populations, species, trophic species, families) allows us to
-represent networks at broader scales, which impacts the properties and
-behaviour of these systems (\textbf{Guimaraes2020StrEco?}). A network's
-nodes can thus designate distinct levels of organization, whereas the
-edges linking these nodes can describe a variety of interaction
-measures. When using a Boolean (yes-no) representation of biotic
-interactions, the observation that one individual from group (or node)
-\(i\) interacts with another individual from group \(j\) is enough to
-set the interaction \(A_{i,j}\) to 1. This simplified representation of
-food webs is a highly valuable source of ecological information
-(\textbf{Pascual2006EcoNet?}) even though it overlooks important factors
-regarding interaction strengths. These, in turn, can be represented
-using weighted interactions, which better describe the energy flows,
-demographic impacts or frequencies of interactions between nodes
-(\textbf{Berlow2004IntStr?}; \textbf{Borrett2019WalPar?}), with
-\(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\) depending on the measure.
-For example, they can be used to estimate the average number of prey
-individuals consumed by the predators in a given time period. This extra
-amount of ecological information typically comes at a cost of greater
-sampling effort or data requirement in predictive models (Strydom
-\emph{et al.} 2021), which can lead to high uncertainties when building
-these types of networks. Therefore, important methodological and
-conceptual decisions must be made when sampling and building food webs.
+individuals that interact with each others (e.g., by predation; Elton
+2001), forming individual-based networks. The aggregation of these
+individuals into more or less homogeneous groups (e.g., populations,
+species, trophic species, families) allows us to represent networks at
+broader scales, which impacts the properties and behaviour of these
+systems (Guimarães 2020). A network's nodes can thus designate distinct
+levels of organization, whereas the edges linking these nodes can
+describe a variety of interaction measures. When using a Boolean
+(yes-no) representation of biotic interactions, the observation that one
+individual from group (or node) \(i\) interacts with another individual
+from group \(j\) is enough to set the interaction \(A_{i,j}\) to 1. This
+simplified representation of food webs is a highly valuable source of
+ecological information (Pascual \emph{et al.} 2006) even though it
+overlooks important factors regarding interaction strengths. These, in
+turn, can be represented using weighted interactions, which better
+describe the energy flows, demographic impacts or frequencies of
+interactions between nodes (Berlow \emph{et al.} 2004; Borrett \&
+Scharler 2019), with \(A_{i,j} \in \mathbb{N}\) or \(\mathbb{R}\)
+depending on the measure. For example, they can be used to estimate the
+average number of prey individuals consumed by the predators in a given
+time period. This extra amount of ecological information typically comes
+at a cost of greater sampling effort or data requirement in predictive
+models (Strydom \emph{et al.} 2021), which can lead to high
+uncertainties when building these types of networks. Therefore,
+important methodological and conceptual decisions must be made when
+sampling and building food webs.
 
@@
 taxonomic misidentifications and ecological misinterpretations (e.g.,
-due to cryptic species and interactions; \textbf{Pringle2020ResFoo?}),
+due to cryptic species and interactions; Pringle \& Hutchinson 2020),
 many observations of interactions are actually false positives.
@@
 probability of interaction, because it impacts the probability that
-species will randomly encounter (Poisot \emph{et al.} 2015;
-\textbf{Canard2012EmeStr?}; \textbf{Canard2014EmpEva?}). Here, we will
-use the variable \(\Omega\) as a substitute for the biological and
-ecological context in which interaction probabilities were estimated.
-This gives us the following equation for the probability of realized
-interaction between species (or taxa) \(i\) and \(j\) in a local network
-\(N\):
+species will randomly encounter (Canard \emph{et al.} 2012; Canard
+\emph{et al.} 2014; Poisot \emph{et al.} 2015). Here, we will use the
+variable \(\Omega\) as a substitute for the biological and ecological
+context in which interaction probabilities were estimated. This gives us
+the following equation for the probability of realized interaction
+between species (or taxa) \(i\) and \(j\) in a local network \(N\):
 
@@
 networks of potential interactions). Second, the structure of local
-networks is constrained by the one of their metaweb
-(\textbf{Saravia2022EcoNet?}). This suggests that a metaweb not only
-constrains the pairwise interactions of its corresponding local
-networks, but also their emerging properties. Inferring the structure of
-local networks from the metaweb could thus help estimate more
-realistically the likelihood that potential interactions are realized
-and observed locally (Strydom \emph{et al.} 2021).
+networks is constrained by the one of their metaweb (Saravia \emph{et
+al.} 2022). This suggests that a metaweb not only constrains the
+pairwise interactions of its corresponding local networks, but also
+their emerging properties. Inferring the structure of local networks
+from the metaweb could thus help estimate more realistically the
+likelihood that potential interactions are realized and observed locally
+(Strydom \emph{et al.} 2021).
 
@@
 
+\leavevmode\hypertarget{ref-Araujo2011Usinga}{}%
+Araujo, M.B., Rozenfeld, A., Rahbek, C. \& Marquet, P.A. (2011). Using
+species co-occurrence networks to assess the impacts of climate change.
+\emph{Ecography}, 34, 897--908.
+
+\leavevmode\hypertarget{ref-Berlow2004Interaction}{}%
+Berlow, E.L., Neutel, A.-M., Cohen, J.E., De Ruiter, P.C., Ebenman, B.,
+Emmerson, M., \emph{et al.} (2004). Interaction strengths in food webs:
+Issues and opportunities. \emph{Journal of Animal Ecology}, 73,
+585--598.
+
 \leavevmode\hypertarget{ref-Blanchet2020Cooccurrencea}{}%
@@
 1050--1063.
+
+\leavevmode\hypertarget{ref-Borrett2019Walk}{}%
+Borrett, S.R. \& Scharler, U.M. (2019). Walk partitions of flow in
+Ecological Network Analysis: Review and synthesis of methods and
+indicators. \emph{Ecological Indicators}, 106, 105451.
+
+\leavevmode\hypertarget{ref-Canard2014Empiricala}{}%
+Canard, E.F., Mouquet, N., Mouillot, D., Stanko, M., Miklisova, D. \&
+Gravel, D. (2014). Empirical Evaluation of Neutral Interactions in
+Host-Parasite Networks. \emph{The American Naturalist}, 183, 468--479.
+
+\leavevmode\hypertarget{ref-Canard2012Emergencea}{}%
+Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
+Mouillot, D. (2012). Emergence of Structural Patterns in Neutral Trophic
+Networks. \emph{PLOS ONE}, 7, e38295.
 
@@
 
+\leavevmode\hypertarget{ref-Delmas2019Analysing}{}%
+Delmas, E., Besson, M., Brice, M.-H., Burkle, L.A., Dalla Riva, G.V.,
+Fortin, M.-J., \emph{et al.} (2019). Analysing ecological networks of
+species interactions. \emph{Biological Reviews}, 94, 16--36.
+
 \leavevmode\hypertarget{ref-Dunne2006Network}{}%
@@
 J.A. \& Pascual, M.). Oxford University Press, pp. 27--86.
+
+\leavevmode\hypertarget{ref-Elton2001Animal}{}%
+Elton, C.S. (2001). \emph{Animal Ecology}. University of Chicago Press,
+Chicago, IL.
 
@@
 
+\leavevmode\hypertarget{ref-Godsoe2022Species}{}%
+Godsoe, W., Murray, R. \& Iritani, R. (2022). Species interactions and
+diversity: A unified framework using Hill numbers. \emph{Oikos}, n/a,
+e09282.
+
 \leavevmode\hypertarget{ref-Gonzalez-Varo2016Labilea}{}%
@@
 700--710.
+
+\leavevmode\hypertarget{ref-Guimaraes2020Structurea}{}%
+Guimarães, P.R. (2020). The Structure of Ecological Networks Across
+Levels of Organization. \emph{Annual Review of Ecology, Evolution, and
+Systematics}, 51, 433--460.
 
@@
 
+\leavevmode\hypertarget{ref-Ohlmann2019Diversity}{}%
+Ohlmann, M., Miele, V., Dray, S., Chalmandrier, L., O'Connor, L. \&
+Thuiller, W. (2019). Diversity indices for ecological networks: A
+unifying framework using Hill numbers. \emph{Ecology Letters}, 22,
+737--747.
+
 \leavevmode\hypertarget{ref-Olesen2010Missing}{}%
@@
 Sciences}, 278, 725--732.
+
+\leavevmode\hypertarget{ref-Pascual2006Ecologicala}{}%
+Pascual, M., Dunne, J.A. \& Dunne, J.A. (2006). \emph{Ecological
+Networks: Linking Structure to Dynamics in Food Webs}. Oxford University
+Press, USA.
 
@@
 
+\leavevmode\hypertarget{ref-Pringle2020Resolving}{}%
+Pringle, R.M. \& Hutchinson, M.C. (2020). Resolving Food-Web Structure.
+\emph{Annual Review of Ecology, Evolution, and Systematics}, 51, 55--80.
+
+\leavevmode\hypertarget{ref-Proulx2005Networka}{}%
+Proulx, S.R., Promislow, D.E.L. \& Phillips, P.C. (2005). Network
+thinking in ecology and evolution. \emph{Trends in Ecology \&
+Evolution}, SPECIAL issue: BUMPER book REVIEW, 20, 345--353.
+
 \leavevmode\hypertarget{ref-Pulliam1974Theory}{}%
@@
 Naturalist}, 108, 59--74.
+
+\leavevmode\hypertarget{ref-Saravia2022Ecological}{}%
+Saravia, L.A., Marina, T.I., Kristensen, N.P., De Troch, M. \& Momo,
+F.R. (2022). Ecological network assembly: How the regional metaweb
+influences local food webs. \emph{Journal of Animal Ecology}, 91,
+630--642.
 

### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@e2e56a3bd52288cdebb8b5b7975ec80364fd35a7 🚀

@@
 be manifested through the effect of sampling effort on the observation
-of interactions (McLeod \emph{et al.} 2021;
-\textbf{Jordano2016Samplinga?}) or of time itself on their realization
-(Poisot \emph{et al.} 2012). There are many network-area relationships
-(e.g., Wood \emph{et al.} 2015; Galiana \emph{et al.} 2018) and
-interaction accumulation curves (e.g, \textbf{Jordano2016Samplinga?})
-explored in the literature. These could inspire the development and
-testing of different equations describing the spatiotemporal scaling of
-probabilistic pairwise interactions in local networks, which are over
+of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
+itself on their realization (Poisot \emph{et al.} 2012). There are many
+network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
+\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
+2016) explored in the literature. These could inspire the development
+and testing of different equations describing the spatiotemporal scaling
+of probabilistic pairwise interactions in local networks, which are over
 the scope of this manuscript.
@@
 
+\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
+Jordano, P. (2016). Sampling networks of ecological interactions.
+\emph{Functional Ecology}, 30, 1883--1893.
+
 \leavevmode\hypertarget{ref-Jordano2003Invarianta}{}%

### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@d0abb50158ae5e1a5c104ffcbbf979a0b5a01093 🚀

@@
 webs are still being laid, there is no clear definition found in the
-literature. This is worrisome, since working with probabilistic species
-interactions without clear guidelines could be misleading as much for
-field ecologists as for computational ecologists who use and generate
-these data. In this contribution, we outline different ways to define
-and interpret interactions probabilities in network ecology and propose
-an approach to thinking about them. These definitions mostly depend on
-the study system (e.g.~local network or metaweb) and on the method used
-to generate them. We show that different definitions can have different
-ecological implications, especially regarding spatial, temporal, and
-taxonomic scaling. Although we will focus on food webs, our observations
-and advice can be applied to all types of ecological networks, from
-plant-pollinator to host-parasite networks. Specifically, we argue that
-probabilities should be better documented, defined mathematically, and
-used with caution when describing species interactions.
+literature or data standard when it comes to publishing data on
+probabilistic interactions (see Salim \emph{et al.} 2022 for a
+discussion on data standardization for mutualistic networks). This is
+worrisome, since working with probabilistic species interactions without
+clear guidelines could be misleading as much for field ecologists as for
+computational ecologists who use and generate these data. In this
+contribution, we outline different ways to define and interpret
+interactions probabilities in network ecology and propose an approach to
+thinking about them. These definitions mostly depend on the study system
+(e.g.~local network or metaweb) and on the method used to generate them.
+We show that different definitions can have different ecological
+implications, especially regarding spatial, temporal, and taxonomic
+scaling. Although we will focus on food webs, our observations and
+advice can be applied to all types of ecological networks, from
+plant-pollinator to host-parasite networks. Indeed, all ecological
+networks, whether they are unipartite or bipartite, share fundamental
+commonalities in their biological conceptualization and mathematical
+representation that support these comparisons (i.e., they all describe
+groups of individuals interacting with each other). Regardless of the
+study system, we argue that probabilities should be better documented,
+defined mathematically, and used with caution when describing species
+interactions.
 
@@
 average number of prey individuals consumed by the predators in a given
-time period. This extra amount of ecological information typically comes
-at a cost of greater sampling effort or data requirement in predictive
-models (Strydom \emph{et al.} 2021), which can lead to high
-uncertainties when building these types of networks. Therefore,
-important methodological and conceptual decisions must be made when
-sampling and building food webs.
+time period (e.g., the average number of fish in the stomach of a
+piscivorous species). Interaction strengths can also be used as good
+estimators of the parameters describing species interactions in a
+Lotka-Volterra model (e.g., Emmerson \& Raffaelli 2004). This extra
+amount of ecological information typically comes at a cost of greater
+sampling effort or data requirement in predictive models (Strydom
+\emph{et al.} 2021), which can lead to high uncertainties when building
+these types of networks. Therefore, important methodological and
+conceptual decisions must be made when sampling and building food webs.
 
@@
 frequencies of interactions between pairs of nodes, with \(\lambda\)
-being the expected rate of interaction. The definition and
-interpretation of parameters like \(p\) and \(\lambda\) are inextricably
-linked to environmental and biological factors such as species relative
-abundance, traits, area, and time, depending on the type of interaction.
+being the expected rate of interaction. Note that weighted interactions
+can be converted to probabilistic interactions by normalizing. The
+definition and interpretation of parameters like \(p\) and \(\lambda\)
+are inextricably linked to environmental and biological factors such as
+species relative abundance, traits, area, and time, depending on the
+type of interaction.\\
 Because Boolean species interactions are much more documented in the
@@
 probability that two taxa can interact regardless of biological
-plasticity, environmental variability or co-occurrence. They are the
-network analogue to the species pool, where local networks originate
+plasticity, environmental variability or co-occurrence. Instead of
+describing stochastic biological processes occurring in nature,
+probabilistic potential interactions can be thought of as a measure of
+imperfect knowledge about the capacity of two taxa to interact. They are
+the network analogue to the species pool, where local networks originate
 from a subset of both species (nodes) and interactions (edges). For this
@@
 within a given time period; in other words, they are context dependant.
-To be specific, space is defined here as the geographic coordinates
-\((x, y)\) of the spatial boundaries delineating the system, whereas
-time is the time interval \(t\) during which interactions were sampled
-or for which they were predicted. We want to point out that they are not
-single values, but rather continued dimensions that could be outlined
-differently depending on the study system. Regardless of how they were
-defined, they always delineate a specific area \(A\) and duration \(t\).
-These could refer to the sampled area and duration or to the targeted
-location and time period.
+They could also represent the likelihood of observing these interactions
+within a given area and time. To be specific, space is defined here as
+the geographic coordinates \((x, y)\) of the spatial boundaries
+delineating the system, whereas time is the time interval \(t\) during
+which interactions were sampled or for which they were predicted. We
+want to point out that they are not single values, but rather continued
+dimensions that could be outlined differently depending on the study
+system. Regardless of how they were defined, they always delineate a
+specific area \(A\) and duration \(t\). These could refer to the sampled
+area and duration or to the targeted location and time period.
 
@@
 variable \(\Omega\) as a substitute for the biological and ecological
-context in which interaction probabilities were estimated. This gives us
-the following equation for the probability of realized interaction
-between species (or taxa) \(i\) and \(j\) in a local network \(N\):
+context in which interaction probabilities were estimated, including the
+presence of higher-order interactions. This gives us the following
+equation for the probability of realized interaction between species (or
+taxa) \(i\) and \(j\) in a local network \(N\):
 
@@
 co-occurrence \(C\) and specific environmental and biological conditions
-\(\Omega\).
+\(\Omega\). These conditions do not systematically need to be specified
+for all studies. However, when they are, they should be made explicit in
+the metadada.
 
@@
 
-\hypertarget{from-potential-to-realized-interactions}{%
-\subsection{From potential to realized
-interactions}\label{from-potential-to-realized-interactions}}
+\hypertarget{applications-of-probabilistic-interactions-data}{%
+\section{Applications of probabilistic interactions
+data}\label{applications-of-probabilistic-interactions-data}}
+
+\hypertarget{inferring-probabilistic-local-food-webs-from-metawebs}{%
+\subsection{Inferring probabilistic local food webs from
+metawebs}\label{inferring-probabilistic-local-food-webs-from-metawebs}}
 
@@
 
-\hypertarget{scaling}{%
-\section{Scaling}\label{scaling}}
-
-\hypertarget{spatial-and-temporal-scales}{%
-\subsection{Spatial and temporal
-scales}\label{spatial-and-temporal-scales}}
-
-Metawebs and local networks intrinsically differ in their relation to
-scale. On one hand, as mentioned above, probabilistic metawebs are
-context independent, i.e., probabilistic pairwise interactions do not
-scale with space and time because they depend solely on the biological
-capacity of the two taxa to interact. This implies that the estimated
-likelihood that two species can potentially interact should be the same
-among all metawebs in which they are present. In practice, this is
-rarely the case because ecologists use different methods and data to
-estimate these probabilities of interactions. However, in the case where
-local metawebs \(M_{x,y}\) are subsampled from their regional
-counterpart \(M_0\), we should expect edge values to be identical among
-all networks, regardless of their spatial scale,
-i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
-other hand, local probabilistic networks are indissociable from their
-spatial and temporal contexts because there are more opportunities of
-interactions (e.g., more individuals, more trait variations, more chance
-of encounter) in a larger area and longer time period (McLeod \emph{et
-al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
-an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
-\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
-to scale spatially, i.e.
-\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
-Similarly, the temporal scaling of probabilistic local food webs could
-be manifested through the effect of sampling effort on the observation
-of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
-itself on their realization (Poisot \emph{et al.} 2012). There are many
-network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
-\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
-2016) explored in the literature. These could inspire the development
-and testing of different equations describing the spatiotemporal scaling
-of probabilistic pairwise interactions in local networks, which are over
-the scope of this manuscript.
+\hypertarget{sampling-random-draws-from-probabilistic-food-webs}{%
+\subsection{Sampling random draws from probabilistic food
+webs}\label{sampling-random-draws-from-probabilistic-food-webs}}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Making interaction probabilities spatiotemporally explicit
-\end{itemize}
+\hypertarget{describing-the-spatial-and-temporal-scaling-of-probabilistic-interactions}{%
+\subsection{Describing the spatial and temporal scaling of probabilistic
+interactions}\label{describing-the-spatial-and-temporal-scaling-of-probabilistic-interactions}}
+
+Metawebs and local networks intrinsically differ in their relation to
+scale. On one hand, as mentioned above, probabilistic metawebs are
+context independent, i.e., probabilistic pairwise interactions do not
+scale with space and time because they depend solely on the biological
+capacity of the two taxa to interact. This implies that the estimated
+likelihood that two species can potentially interact should be the same
+among all metawebs in which they are present. In practice, this is
+rarely the case because ecologists use different methods and data to
+estimate these probabilities of interactions (e.g., different sampling
+area and time period). However, in the case where local metawebs
+\(M_{x,y}\) are subsampled from their regional counterpart \(M_0\), we
+should expect edge values to be identical among all networks, regardless
+of their spatial scale,
+i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
+other hand, local probabilistic networks are indissociable from their
+spatial and temporal contexts because there are more opportunities of
+interactions (e.g., more individuals, more trait variations, more chance
+of encounter) in a larger area and longer time period (McLeod \emph{et
+al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
+an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
+\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
+to scale spatially,
+i.e.~\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
+Similarly, the temporal scaling of probabilistic local food webs could
+be manifested through the effect of sampling effort on the observation
+of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
+itself on their realization (Poisot \emph{et al.} 2012). There are many
+network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
+\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
+2016) explored in the literature. These could inspire the development
+and testing of different equations describing the spatiotemporal scaling
+of probabilistic pairwise interactions in local networks, which are over
+the scope of this manuscript.
 
@@
 
-\hypertarget{taxonomic-scale}{%
-\subsection{Taxonomic scale}\label{taxonomic-scale}}
+\hypertarget{making-probabilistic-interactions-spatiotemporally-explicit}{%
+\subsection{Making probabilistic interactions spatiotemporally
+explicit}\label{making-probabilistic-interactions-spatiotemporally-explicit}}
+
+The variability of species interactions spurred the development of
+methods aiming at predicting ecological networks at fine spatial and
+temporal scales. For example, Bohan \emph{et al.} (2017) proposed a
+framework to reconstruct networks in real time using continuous
+biomonitoring. Here, we will build on these studies by proposing a
+simple model to make probabilistic local networks spatiotemporally
+explicit. These types of models could prove useful when inferring food
+webs across time and space from sparse data. However, they are not
+suitable for metawebs, which are static objects.
+
+One way that probabilistic food webs can be made spatiotemporally
+explicit is by modelling interactions between co-occurring species as a
+Poisson process with rate \(\lambda\). Specifically, if the total
+observation time for a location is \(t_0\), the probability that two
+co-occurring species \(i\) and \(j\) will interact during this time
+period is
+\(P_N(i \rightarrow j | C_{i,j} = 1, t = t_0) = 1-e^{-\lambda t_0}\),
+which approaches \(1\) when \(t \to \infty\). The value of the parameter
+\(\lambda\) could be estimated using prior data on interaction
+strengths, if available. Additionally, we can estimate the probability
+of co-occurrence at location \((x,y)\) with
+\(P_{x,y}(C_{i,j} = 1) = P_{x,y}(i) P_{x,y}(j)\gamma\), where
+\(P_{x,y}(i)\) and \(P_{x,y}(j)\) are respectively the probabilities of
+occurrence of species \(i\) and \(j\) and \(\gamma\) is the strength of
+association between occurrence and co-occurrence, as defined in Cazelles
+\emph{et al.} (2016). Note that in empirical networks, \(\gamma\) is
+typically \(> 1\) (Catchen \emph{et al.} 2023). The observation of this
+interaction would thus follow a Bernoulli distribution with parameter
+\(p = p_A(x,y)p_B(x,y)\gamma(1-e^{-\lambda t_0})\). This simple model
+could be customized in many ways, e.g.~by linking \(\lambda\) with given
+environmental variables or by adding in observation errors (i.e.,
+probability of false negatives and false positives; Catchen \emph{et
+al.} (2023)).
+
+\hypertarget{exploring-different-levels-of-organization}{%
+\subsection{Exploring different levels of
+organization}\label{exploring-different-levels-of-organization}}
 
@@
 \item
+  Why would we want to scale networks taxonomically?
+\item
+  Do all nodes need to be the same taxonomic scale, within a network?
+\item
   How is it similar and different to spatial and temporal scaling?
@@
   individuals or nodes.
+\item
+  Papers: Vázquez \emph{et al.} (2022)
 \end{itemize}
@@
 way to a better assessment of the spatiotemporal variability and
-uncertainty of biotic interactions. However, we showed that network
-metadata are perhaps as important as interaction data themselves when it
-comes to interpreting probabilistic food webs in ecological terms.
-First, the type of probabilistic interaction (potential or realized)
-impacts the importance of scale, with interactions in metawebs being
-scale independent, both spatially and temporally. Second, the conditions
-in which local networks were estimated (e.g., area, time, biological and
-environmental factors) and the attributes of the interacting species
-that were considered (e.g., species co-occurrence) are essential
-contextual factors that impact the mathematical representation of
-probabilities and their resulting behaviour. Third, the biological
-interpretation of probabilities changes with the level of organization
-of the network due to the aggregation of individuals into broader
-groups. All these information should be available as clear metadata so
-that ecologists can use probabilistic network data appropriately.
+uncertainty of biotic interactions. However, measuring probabilities
+empirically can be strenuous given the difficulties of deciphering
+species and interactions (Pringle \& Hutchinson 2020). In this context,
+the development of computational methods makes it possible to estimate
+interaction probabilities at large scales, which in turn can pinpoint
+where we should go to optimise our sampling effort for better resolving
+local food webs.
+
+In this contribution, we showed that network metadata are perhaps as
+important as interaction data themselves when it comes to interpreting
+probabilistic food webs in ecological terms. First, the type of
+probabilistic interaction (potential or realized) impacts the importance
+of scale, with interactions in metawebs being scale independent, both
+spatially and temporally. Second, the conditions in which local networks
+were estimated (e.g., area, time, biological and environmental factors)
+and the attributes of the interacting species that were considered
+(e.g., species co-occurrence) are essential contextual factors that
+impact the mathematical representation of probabilities and their
+resulting behaviour. Third, the biological interpretation of
+probabilities changes with the level of organization of the network due
+to the aggregation of individuals into broader groups. All these
+information should be available as clear metadata so that ecologists can
+use probabilistic network data appropriately.
 
@@
 
+\leavevmode\hypertarget{ref-Bohan2017NexGlo}{}%
+Bohan, D.A., Vacher, C., Tamaddoni-Nezhad, A., Raybould, A., Dumbrell,
+A.J. \& Woodward, G. (2017). Next-Generation Global Biomonitoring:
+Large-scale, Automated Reconstruction of Ecological Networks.
+\emph{Trends in Ecology \& Evolution}, 32, 477--487.
+
 \leavevmode\hypertarget{ref-Borrett2019Walk}{}%
@@
 Chicago, IL.
+
+\leavevmode\hypertarget{ref-Emmerson2004PrePre}{}%
+Emmerson, M.C. \& Raffaelli, D. (2004). Predatorprey body size,
+interaction strength and the stability of a real food web. \emph{Journal
+of Animal Ecology}, 73, 399--409.
 
@@
 
+\leavevmode\hypertarget{ref-Salim2022DatSta}{}%
+Salim, J.A., Saraiva, A.M., Zermoglio, P.F., Agostini, K., Wolowski, M.,
+Drucker, D.P., \emph{et al.} (2022). Data standardization of
+plantpollinator interactions. \emph{GigaScience}, 11, giac043.
+
 \leavevmode\hypertarget{ref-Saravia2022Ecological}{}%
@@
 
+\leavevmode\hypertarget{ref-VazquezSS2022EcoInt}{}%
+Vázquez, D.P., Peralta, G., Cagnolo, L., Santos, M. \& Igual, E. autores
+contribuyeron por. (2022). Ecological interaction networks. What we
+know, what we don't, and why it matters. \emph{Ecología Austral}, 32,
+670--697.
+
 \leavevmode\hypertarget{ref-Wood2015Effects}{}%

### 2023-02-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@b99dd7488628b3c5d215763948b80c5c39ca193c 🚀

@@
 species relative abundance, traits, area, and time, depending on the
-type of interaction.\\
-Because Boolean species interactions are much more documented in the
-literature, our primary focus in this contribution will be on addressing
-the challenges in defining and interpretating \(p\) for pairwise species
-interactions.
+type of interaction. Because Boolean species interactions are much more
+documented in the literature, our primary focus in this contribution
+will be on addressing the challenges in defining and interpretating
+\(p\) for pairwise species interactions.
 
@@
 
-\hypertarget{exploring-different-levels-of-organization}{%
-\subsection{Exploring different levels of
-organization}\label{exploring-different-levels-of-organization}}
+\hypertarget{exploring-different-taxonomic-resolutions}{%
+\subsection{Exploring different taxonomic
+resolutions}\label{exploring-different-taxonomic-resolutions}}
 
-How do interaction probabilities scale taxonomically?
+The properties of ecological networks depend on their level of
+organization (Guimarães 2020). Indeed, at different taxonomic scales,
+different behaviours and dynamics can be observed and distinct
+ecological questions can be answered (e.g., exploring evolutionary
+dynamics at broad taxonomic scales). Because of these reasons, it could
+be important to analyse the same network at different taxonomic scales.
+However, we want to emphasize here that many networks do not have an
+homogenous level of organisation (Vázquez \emph{et al.} 2022). Indeed,
+different nodes within the same network can be represented at different
+taxonomic scales (e.g., a network composed of species and trophic
+species). This becomes important when we consider that the biological
+interpretation of interaction probabilities depends on the nodes'
+resolution. For example, in individual-based networks, the probability
+that two individuals interact could represent the degree of belief that
+one will actually consume the other. In species-based networks, the
+probability that two species interact could rather represent the degree
+of belief that \emph{at least} one individual from the predator species
+will eat \emph{at least} another individual from the prey species. This
+distinction in interpretation impacts the way probability values change
+with taxonomic scale.
 
-\begin{itemize}
-\tightlist
-\item
-  There are different biological interpretations of probabilities in
-  food webs at the individual level and at higher taxonomic levels.
-\item
-  How does the scaling up of the nodes from an individual to population
-  to any higher taxonomic group change our interpretation of interaction
-  probabilities? How does the aggregation change our interpretation?
-\item
-  Why would we want to scale networks taxonomically?
-\item
-  Do all nodes need to be the same taxonomic scale, within a network?
-\item
-  How is it similar and different to spatial and temporal scaling?
-  Basically, all kinds of scaling are just different ways to aggregate
-  individuals or nodes.
-\item
-  Papers: Vázquez \emph{et al.} (2022)
-\end{itemize}
+There are a lot of similarities between taxonomic and spatiotemporal
+scaling of probabilistic interactions. Fundamentally, these types of
+scaling are just different ways to aggregate individuals into broader
+nodes, either spatially, temporally, or taxonomically. However, there
+are also important differences between them. First, in metawebs, if we
+know that two species have the capacity to interact, we can infer that
+their respective genus should also be able to interact (i.e., there
+should be at least two individuals within these genus that can
+interact). On the contrary, knowing that two genus can interact does not
+mean that all pairwise combinations of species within these genus can
+also interact among themselves. This observation also applies to local
+networks. When it comes to probabilistic networks, interaction
+probabilities at broader taxonomic scales can be directly obtained from
+probabilities at finer scales when aggregating nodes. For example, if we
+have in a network \(n_A\) species from genus \(A\) and \(n_B\) species
+from genus \(B\), we can calculate the probability that the two genus
+interact as
+\(P_N(A \rightarrow B) = 1 - \prod_{i = 1}^{n_1}\prod_{j = 1}^{n_2}(1 - P_N(A_i \rightarrow B_j))\),
+where \(A_i\) and \(B_j\) are the species of the corresponding genus.
+However, more sophisticated models need to be used when building
+probabilistic networks at smaller taxonomic resolutions (e.g., when
+building a species-level network from a genus-level network). One could,
+for example, estimate the probabilities of all pairwise species
+interactions by using a Beta distribution parametrised by the
+broader-scale network.
 

### 2023-02-13 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@b99dd7488628b3c5d215763948b80c5c39ca193c 🚀

@@
 
-\hypertarget{exploring-different-levels-of-organization}{%
-\subsection{Exploring different levels of
-organization}\label{exploring-different-levels-of-organization}}
-
-How do interaction probabilities scale taxonomically?
-
-\begin{itemize}
-\tightlist
-\item
-  There are different biological interpretations of probabilities in
-  food webs at the individual level and at higher taxonomic levels.
-\item
-  How does the scaling up of the nodes from an individual to population
-  to any higher taxonomic group change our interpretation of interaction
-  probabilities? How does the aggregation change our interpretation?
-\item
-  Why would we want to scale networks taxonomically?
-\item
-  Do all nodes need to be the same taxonomic scale, within a network?
-\item
-  How is it similar and different to spatial and temporal scaling?
-  Basically, all kinds of scaling are just different ways to aggregate
-  individuals or nodes.
-\item
-  Papers: Vázquez \emph{et al.} (2022)
-\end{itemize}
+\hypertarget{exploring-different-taxonomic-resolutions}{%
+\subsection{Exploring different taxonomic
+resolutions}\label{exploring-different-taxonomic-resolutions}}
+
+The properties of ecological networks depend on their level of
+organization (Guimarães 2020). Indeed, at different taxonomic scales,
+different behaviours and dynamics can be observed and distinct
+ecological questions can be answered (e.g., exploring evolutionary
+dynamics at broad taxonomic scales). Because of these reasons, it could
+be important to analyse the same network at different taxonomic scales.
+However, we want to emphasize here that many networks do not have an
+homogenous level of organisation (Vázquez \emph{et al.} 2022). Indeed,
+different nodes within the same network can be represented at different
+taxonomic scales (e.g., a network composed of species and trophic
+species). This becomes important when we consider that the biological
+interpretation of interaction probabilities depends on the nodes'
+resolution. For example, in individual-based networks, the probability
+that two individuals interact could represent the degree of belief that
+one will actually consume the other. In species-based networks, the
+probability that two species interact could rather represent the degree
+of belief that \emph{at least} one individual from the predator species
+will eat \emph{at least} another individual from the prey species. This
+distinction in interpretation impacts the way probability values change
+with taxonomic scale.
+
+There are a lot of similarities between taxonomic and spatiotemporal
+scaling of probabilistic interactions. Fundamentally, these types of
+scaling are just different ways to aggregate individuals into broader
+nodes, either spatially, temporally, or taxonomically. However, there
+are also important differences between them. First, in metawebs, if we
+know that two species have the capacity to interact, we can infer that
+their respective genus should also be able to interact (i.e., there
+should be at least two individuals within these genus that can
+interact). On the contrary, knowing that two genus can interact does not
+mean that all pairwise combinations of species within these genus can
+also interact among themselves. This observation also applies to local
+networks. When it comes to probabilistic networks, interaction
+probabilities at broader taxonomic scales can be directly obtained from
+probabilities at finer scales when aggregating nodes. For example, if we
+have in a network \(n_A\) species from genus \(A\) and \(n_B\) species
+from genus \(B\), we can calculate the probability that the two genus
+interact as
+\(P_N(A \rightarrow B) = 1 - \prod_{i = 1}^{n_1}\prod_{j = 1}^{n_2}(1 - P_N(A_i \rightarrow B_j))\),
+where \(A_i\) and \(B_j\) are the species of the corresponding genus.
+However, more sophisticated models need to be used when building
+probabilistic networks at smaller taxonomic resolutions (e.g., when
+building a species-level network from a genus-level network). One could,
+for example, estimate the probabilities of all pairwise species
+interactions by using a Beta distribution parametrised by the
+broader-scale network.
 

### 2023-02-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@fa8c450e206c47e724b12556ba4c4ee3995ddd4c 🚀

@@
 interact as
-\(P_N(A \rightarrow B) = 1 - \prod_{i = 1}^{n_1}\prod_{j = 1}^{n_2}(1 - P_N(A_i \rightarrow B_j))\),
+\(P_N(A \rightarrow B) = 1 - \prod_{i = 1}^{n_A}\prod_{j = 1}^{n_B}(1 - P_N(A_i \rightarrow B_j))\),
 where \(A_i\) and \(B_j\) are the species of the corresponding genus.

### 2023-02-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@dd36a91250906a6bedb7e29e5fa0f81b6bd71ae7 🚀

@@
 draws). This has direct implications on the spatial scaling of
-interactions. For example, let \(N_2\) be another network of area
-\(A_2 < A_0\) within \(A_0\) and disjoint from \(N_1\), such as \(N_1\)
-and \(N_2\) form \(N_0\) (think of two contiguous cells that together
-delineate \(N_0\)). All other things being equal, we should expect the
-probability that \(i\) and \(j\) interacts in \(A_0\) to be
+interactions. For example, let \(N_1\) and \(N_2\) be networks of area
+\(< A_0\) within a bigger area \(A_0\) and disjoint from each other,
+such as \(N_1\) and \(N_2\) form \(N_0\) (think of two contiguous cells
+that together delineate \(N_0\)). All other things being equal, we
+should expect the probability that \(i\) and \(j\) interacts in \(A_0\)
+to be
 \(P_{N_0}(i \rightarrow j) = 1 - (1 - P_{N_1}(i \rightarrow j)) \times (1 - P_{N_2}(i \rightarrow j))\)
